---
title: "Analyses of learning via shared features experiments"
author: "Ian Hussey"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    code_folding: hide
    highlight: haddock
    number_sections: no
    theme: flatly
    toc: yes
    toc_float: yes
---

# To do

sean:

- check levels of CS1 vs CS2 for exp 5
- missing data for Participant 567's Color_Matching variable in exp 4. - ISSUE 1
- ISSUE 2 - exps 2 and 4 have IAT_Score_recoded, what is it and should i be using it?
- ISSUE 3 Color matching uses the wrong levels, unclear whehter morag is CS1 or 2
- robustness tests are faked for the moment: remove commented out filters from the robustness tests throughtout to make them work - needs the awareness variables in the data to make this work.

```{r, include=FALSE}
knitr::opts_chunk$set(message = FALSE,
                      warning = FALSE)
```

```{r}

# disable scientific notation
options(scipen = 999) 

# dependencies
library(tidyverse)
library(effsize)
library(foreign)
library(timesavers)
library(BayesFactor)
library(weights)
library(sjPlot)
library(nnet)
library(metafor)

```

# Data processing

```{r}

# get data

# convert SPSS to csv
input_data_exp_1 <- 
  read.spss("../experiment 1/data/processed/data_processed.sav", to.data.frame = TRUE)

input_data_exp_2 <- 
  read.spss("../experiment 2/data/processed/data_processed.sav", to.data.frame = TRUE)

input_data_exp_3 <- 
  read.spss("../experiment 3/data/processed/data_processed.sav", to.data.frame = TRUE)

input_data_exp_4 <- 
  read.spss("../experiment 4/data/processed/data_processed.sav", to.data.frame = TRUE)

input_data_exp_5 <- 
  read.spss("../experiment 5/data/processed/data_processed.sav", to.data.frame = TRUE)

write_csv(input_data_exp_1, "../experiment 1/data/processed/data_processed.csv")
write_csv(input_data_exp_2, "../experiment 2/data/processed/data_processed.csv")
write_csv(input_data_exp_3, "../experiment 3/data/processed/data_processed.csv")
write_csv(input_data_exp_4, "../experiment 4/data/processed/data_processed.csv")
write_csv(input_data_exp_5, "../experiment 5/data/processed/data_processed.csv")

# tidy data
tidied_data_exp_1 <- read.csv("../experiment 1/data/processed/data_processed.csv") %>%
  mutate(intention = str_remove_all(Intentions_response, " "),
         intention = str_remove_all(intention, "Iwouldtry"),
         intention = as.factor(intention)) %>%
  select(Participant, 
         Color_Matching,
         IAT_Score,
         EC_Effect_CS1_CS2_Difference_Score,
         intention) %>%
  mutate(Color_Matching = as.factor(str_replace_all(as.character(Color_Matching), " ", "")))

tidied_data_exp_2 <- read.csv("../experiment 2/data/processed/data_processed.csv") %>%
  mutate(intention = str_remove_all(Intention_Ratings, " "),
         intention = str_remove_all(intention, "Iwouldtry"),
         intention = as.factor(intention)) %>%
  select(Participant, 
         Color_Matching,
         IAT_Score,  # why is there an IAT_Score_Transformed present too? what does it refer to? ISSUE 2
         EC_Effect_CS1_CS2_Difference_Score,
         intention) %>%
  mutate(Color_Matching = as.factor(str_replace_all(as.character(Color_Matching), " ", "")))

tidied_data_exp_3 <- read.csv("../experiment 3/data/processed/data_processed.csv") %>%
  mutate(intention = str_remove_all(Intentions_response, " "),
         intention = str_remove_all(intention, "Iwouldtry"),
         intention = as.factor(intention)) %>%
  select(Participant, 
         Color_Matching,
         IAT_Score,
         EC_Effect_CS1_CS2_Difference_Score,
         intention) %>%
  mutate(Color_Matching = as.factor(str_replace_all(as.character(Color_Matching), " ", ""))) %>%
  # ISSUE 4 unused levels
  na.omit() %>%
  mutate(Color_Matching = as.factor(as.character(Color_Matching)))

tidied_data_exp_4 <- read.csv("../experiment 4/data/processed/data_processed.csv") %>%
  mutate(intention = str_remove_all(Intentions_response, " "),
         intention = str_remove_all(intention, "Iwouldtry"),
         intention = as.factor(intention)) %>%
  select(Participant, 
         Color_Matching,
         IAT_Score,  # why is there an IAT_Score_Transformed present too? what does it refer to? ISSUE 2
         EC_Effect_CS1_CS2_Difference_Score,
         intention) %>%
  mutate(Color_Matching = as.factor(str_replace_all(as.character(Color_Matching), " ", ""))) %>%
  # missing data for one participant, throws off factor levels  ############ ISSUE 1
  filter(Participant != 567) %>%
  mutate(Color_Matching = as.factor(as.character(Color_Matching)))

tidied_data_exp_5 <- read.csv("../experiment 5/data/processed/data_processed.csv") %>%
  mutate(intention = str_remove_all(Intentions_response, " "),
         intention = str_remove_all(intention, "Iwouldtry"),
         intention = as.factor(intention)) %>%
  select(Participant, 
         Color_Matching,
         IAT_Score,
         EC_Effect_CS1_CS2_Difference_Score,
         intention) %>%
  mutate(Color_Matching = as.factor(str_replace_all(as.character(Color_Matching), " ", ""))) %>%
  # ISSUE 3 Color matching uses the wrong levels, unclear whehter morag is CS1 or 2
  mutate(Color_Matching = dplyr::recode(Color_Matching,
                                        `Morag_Good_Struan_Bad` = "CS1_Positive_CS2_Negative",
                                        `Struan_Good_Morag_Bad` = "CS2_Positive_CS1_Negative"))

# write to disk
write_csv(tidied_data_exp_1, "../experiment 1/data/processed/data_for_analysis.csv")
write_csv(tidied_data_exp_2, "../experiment 2/data/processed/data_for_analysis.csv")
write_csv(tidied_data_exp_3, "../experiment 3/data/processed/data_for_analysis.csv")
write_csv(tidied_data_exp_4, "../experiment 4/data/processed/data_for_analysis.csv")
write_csv(tidied_data_exp_5, "../experiment 5/data/processed/data_for_analysis.csv")

```

# Analytic strategy

```{r}

# analysis workflow. is applied witin all studies ---------------

# between groups comparisons analysis workflow ------
t_test_analyses <- function(data) {
  
  # summary stats
  summary_stats <- data %>%
    group_by(IV) %>%
    dplyr::summarize(mean = mean(DV),
                     sd = sd(DV)) %>%
    round_df(2)
  
  # t test
  t_test <- t.test(formula = DV ~ IV,
                   alternative = "two.sided",
                   paired = FALSE,
                   data = data)
  
  # effect size
  # formula based cohen's d seems to be invariant to ordering of the levels, can't control whether the direction 
  # cohens_d <- effsize::cohen.d(formula = DV ~ IV,
  #                              paired = FALSE,
  #                              data = data)
  cohens_d <- effsize::cohen.d(data$DV[data$IV == "CS1_Positive_CS2_Negative"],
                               data$DV[data$IV == "CS2_Positive_CS1_Negative"],
                               paired = FALSE)
  
  # printing
  t_test_p <- t_test$p.value[[1]]
  t_test_p_apa <- ifelse(t_test_p < 0.001, "< .001", 
                         ifelse(t_test_p < 0.01,
                                paste("= ", rd(t_test_p, 3), sep = ""),  # rd() rounds, converts to string, and removes the leading 0.
                                paste("= ", rd(t_test_p, 2), sep = "")))
  
  t_test_output <- paste("t(", format(round(t_test$parameter[[1]], 2), nsmall = 2), 
                         ") = ", format(round(t_test$statistic[[1]], 2), nsmall = 2), 
                         ", p ", t_test_p_apa, 
                         ", d = ", format(round(cohens_d$estimate[[1]], 2), nsmall = 2), 
                         ", 95% CI = [", format(round(cohens_d$conf.int[["inf"]], 2), nsmall = 2), ", ", 
                         format(round(cohens_d$conf.int[["sup"]], 2), nsmall = 2), "]", 
                         sep = "")
  
  # bayes factor t test
  t_test_bf <- ttestBF(formula = DV ~ IV,
                       data = data)
  
  bf10 <- round(exp(t_test_bf@bayesFactor$bf), 2)
  
  return(list(summary_stats = summary_stats,
              t_test = t_test,
              cohens_d = cohens_d,
              t_test_output = t_test_output,
              t_test_p = t_test_p,
              t_test_bf = t_test_bf,
              bf10 = bf10))
}

# multinominal analysis workflow ------
multinominal_analysis <- function(data) {
  
  # fit model
  fit <- multinom(intention ~ Color_Matching, 
                  data = data)
  
  # calculate p values
  z <- summary(fit)$coefficients/summary(fit)$standard.errors
  p <- (1 - pnorm(abs(z), 0, 1)) * 2
  
  pvalues <- p %>%
    as.data.frame() %>%
    rownames_to_column(var = "var") %>%
    
    # no idea why this var name contains so many spaces, but it does, so go figure
    rename(p = "Color_MatchingCS2_Positive_CS1_Negative") %>%
    mutate(p = apa_p_value(p)) %>%
    select(p)
  
  # calc odds ratios and CIs
  coefficients <- as.data.frame(summary(fit)$coefficients) %>%
    rownames_to_column(var = "var") %>%
    rename(logOR_Color_Matching = "Color_MatchingCS2_Positive_CS1_Negative") %>%
    select(var, logOR_Color_Matching)
  
  se <- as.data.frame(summary(fit)$standard.errors) %>%
    rownames_to_column(var = "var") %>%
    rename(logOR_se_Color_Matching = "Color_MatchingCS2_Positive_CS1_Negative") %>%
    select(logOR_se_Color_Matching)
  
  # combine
  results <- cbind(coefficients, se) %>%
    mutate(OR = round(exp(logOR_Color_Matching), 2),
           OR_ci_lwr = round(exp(logOR_Color_Matching - logOR_se_Color_Matching*1.96), 2),
           OR_ci_upr = round(exp(logOR_Color_Matching + logOR_se_Color_Matching*1.96), 2)) %>%
    cbind(pvalues) %>%
    rename(logOR = logOR_Color_Matching,
           logOR_se = logOR_se_Color_Matching)
  
  return(results)
}

# meta analysis workflow ------
meta_analysis_workflow <- function(data, 
                                   effect_size_label, 
                                   reference_line, 
                                   exp_estimates = FALSE,
                                   plot = TRUE) {
  require(timesavers)
  require(tidyverse)
  require(metafor)
  
  # fit random effects model 
  fitted_model <- 
    rma(yi = yi, sei = sei,
        data = data,
        slab = Experiment)
  
  p_value <- apa_p_value(fitted_model$pval)
  
  # model predictions
  meta_analysis_results <-
    predict(fitted_model, digits = 5) %>%
    as.data.frame() %>%
    gather() %>%
    round_df(3) %>%
    dplyr::rename(metric = key,
                  estimate = value) %>%
    mutate(metric = dplyr::recode(metric,
                                  "pred" = paste0("Meta analysed ", effect_size_label),
                                  "ci.lb" = "95% CI lower",
                                  "ci.ub" = "95% CI upper",
                                  "cr.lb" = "95% CR lower",
                                  "cr.ub" = "95% CR upper"))
  
  # Color_Matchingally exponentiate estimates if converting log odds to odds ratios
  if(exp_estimates == TRUE) {
    meta_analysis_results <- meta_analysis_results %>%
      mutate(estimate = round(exp(estimate), 3))
  }
  
  meta_analysis_results <- rbind(meta_analysis_results,
                                 data.frame(metric = "p",
                                            estimate = p_value))
  
  # summarize results
  meta_analysis_results_text <- 
    paste0("k = ", fitted_model$k, ", ", 
           effect_size_label, " = ", meta_analysis_results$estimate[1],
           # dynamic indexing of some values as different models return variables in different locations, but relative location is reliable
           ", 95% CI = [", meta_analysis_results$estimate[length(meta_analysis_results$estimate)-4],  
           ", ", meta_analysis_results$estimate[length(meta_analysis_results$estimate)-3], 
           "], 95% CR = [", meta_analysis_results$estimate[length(meta_analysis_results$estimate)-2], 
           ", ", meta_analysis_results$estimate[length(meta_analysis_results$estimate)-1],
           "], p ", meta_analysis_results$estimate[length(meta_analysis_results$estimate)])
  
  heterogeneity_test_results_text <- 
    paste0("Q(df = ",    fitted_model$k - 1, ") = ", round(fitted_model$QE, 2), 
           ", p = ",     ifelse(fitted_model$pval < 0.001, "< .001", as.character(round(fitted_model$pval, 3))),
           ", tau^2 = ", round(fitted_model$tau2, 2), 
           ", I^2 = ",   round(fitted_model$I2, 2),
           ", H^2 = ",   round(fitted_model$H2, 2))
  
  # forest plot
  if (exp_estimates == TRUE) {
    transformation <- exp
  } else { 
    transformation <- NULL
  }
  

  if (plot == TRUE) {
    forest_plot <- forest(fitted_model,
                        xlab = effect_size_label,
                        addcred = TRUE,
                        atransf = transformation,
                        refline = reference_line)
  } else {
    forest_plot <- NULL
  }
  
  
  return(list(fitted_model = fitted_model, 
              meta_analysis_results = meta_analysis_results,
              meta_analysis_results_text = meta_analysis_results_text,
              heterogeneity_test_results_text = heterogeneity_test_results_text,
              forest_plot = forest_plot))
}


# robustness between original test and subset -----------
robust_test <- function(subset_test, original_test) {
  
  subset_p <- subset_test$estimate[subset_test$metric == "p"] %>%
    str_remove(., "=") %>%
    str_remove(., "<") %>%
    str_remove(., " ") %>%
    as.numeric()
  
  original_p <- original_test$estimate[original_test$metric == "p"] %>%
    str_remove(., "=") %>%
    str_remove(., "<") %>%
    str_remove(., " ") %>%
    as.numeric()
  
  return((subset_p >= 0.05 & original_p >= 0.05) | (subset_p < 0.05 & original_p < 0.05))
}

```

# Experiments 

## Experiment 1

### H1: IAT

```{r}

results_exp_1_h1 <- tidied_data_exp_1 %>%
  mutate(DV = IAT_Score,
         IV = Color_Matching) %>%
  t_test_analyses(.)

```

When CS1 eventually shared a color with positive words and CS2 shared a color with negative words, participants showed an automatic relative preference for CS1 over CS2 on the IAT (M = `r format(results_exp_1_h1$summary_stats$mean[results_exp_1_h1$summary_stats$IV == "CS1_Positive_CS2_Negative"], nsmall = 2)`, SD = `r format(results_exp_1_h1$summary_stats$sd[results_exp_1_h1$summary_stats$IV == "CS1_Positive_CS2_Negative"], nsmall = 2)`), whereas when CS1 eventually shared a color with negative words and CS2 shared a color with positive words, they demonstrated a relative preference for CS2 over CS1 (M = `r format(results_exp_1_h1$summary_stats$mean[results_exp_1_h1$summary_stats$IV == "CS2_Positive_CS1_Negative"], nsmall = 2)`, SD = `r format(results_exp_1_h1$summary_stats$sd[results_exp_1_h1$summary_stats$IV == "CS2_Positive_CS1_Negative"], nsmall = 2)`), `r results_exp_1_h1$t_test_output`, BF10 = `r format(results_exp_1_h1$bf10, nsmall = 2)`.

#### Robustness tests

```{r}

full_sample_p_value_exp_1_h1 <- results_exp_1_h1$t_test_p

# re run tests with desired subsets of participants
results_exp_1_h1_contingency_memory <- tidied_data_exp_1 %>%
  #filter(contingency_memory == TRUE) %>%
  mutate(DV = IAT_Score,
         IV = Color_Matching) %>%
  t_test_analyses(.)

results_exp_1_h1_demand_compliance <- tidied_data_exp_1 %>%
  #filter(demand_compliance == FALSE) %>%
  mutate(DV = IAT_Score,
         IV = Color_Matching) %>%
  t_test_analyses(.)

results_exp_1_h1_hypothesis_aware <- tidied_data_exp_1 %>%
  #filter(hypothesis_aware == FALSE) %>%
  mutate(DV = IAT_Score,
         IV = Color_Matching) %>%
  t_test_analyses(.)

results_exp_1_h1_influence_aware <- tidied_data_exp_1 %>%
  #filter(influence_aware == FALSE) %>%
  mutate(DV = IAT_Score,
         IV = Color_Matching) %>%
  t_test_analyses(.)

# robustness strings
robustness_contingency_memory <- 
  ifelse((results_exp_1_h1_contingency_memory$t_test_p < 0.05 & 
            full_sample_p_value_exp_1_h1 < 0.05) |
           (results_exp_1_h1_contingency_memory$t_test_p >= 0.05 & 
              full_sample_p_value_exp_1_h1 >= 0.05), "were", "were not")

robustness_demand_compliance <- 
  ifelse((results_exp_1_h1_demand_compliance$t_test_p < 0.05 & 
            full_sample_p_value_exp_1_h1 < 0.05) |
           (results_exp_1_h1_demand_compliance$t_test_p >= 0.05 & 
              full_sample_p_value_exp_1_h1 >= 0.05), "were", "were not")

robustness_hypothesis_aware <- 
  ifelse((results_exp_1_h1_hypothesis_aware$t_test_p < 0.05 & 
            full_sample_p_value_exp_1_h1 < 0.05) |
           (results_exp_1_h1_hypothesis_aware$t_test_p >= 0.05 & 
              full_sample_p_value_exp_1_h1 >= 0.05), "were", "were not")

robustness_influence_aware <- 
  ifelse((results_exp_1_h1_influence_aware$t_test_p < 0.05 & 
            full_sample_p_value_exp_1_h1 < 0.05) |
           (results_exp_1_h1_influence_aware$t_test_p >= 0.05 & 
              full_sample_p_value_exp_1_h1 >= 0.05), "were", "were not")

```

- Results `r robustness_contingency_memory` robust to including only participants who were contingency aware, p in subsample `r apa_p_value(results_exp_1_h1_contingency_memory$t_test_p)`.
- Results `r robustness_demand_compliance` robust to including only participants who were not demand compliant, p in subsample `r apa_p_value(results_exp_1_h1_demand_compliance$t_test_p)`.
- Results `r robustness_hypothesis_aware` robust to including only participants who were not hypothesis aware, p in subsample `r apa_p_value(results_exp_1_h1_hypothesis_aware$t_test_p)`.
- Results `r robustness_influence_aware` robust to including only participants who were not influence aware, p in subsample `r apa_p_value(results_exp_1_h1_influence_aware$t_test_p)`.

### H2: Self-report ratings

```{r}

results_exp_1_h2 <- tidied_data_exp_1 %>%
  mutate(DV = EC_Effect_CS1_CS2_Difference_Score,
         IV = Color_Matching) %>%
  t_test_analyses(.)

```

When CS1 eventually shared a color with positive words and CS2 shared a color with negative words, participants showed a relative preference on the self-report ratings for CS1 over CS2 (M = `r format(results_exp_1_h2$summary_stats$mean[results_exp_1_h2$summary_stats$IV == "CS1_Positive_CS2_Negative"], nsmall = 2)`, SD = `r format(results_exp_1_h2$summary_stats$sd[results_exp_1_h2$summary_stats$IV == "CS1_Positive_CS2_Negative"], nsmall = 2)`), whereas when CS1 eventually shared a color with negative words and CS2 shared a color with positive words, they demonstrated a relative preference for CS2 over CS1 (M = `r format(results_exp_1_h2$summary_stats$mean[results_exp_1_h2$summary_stats$IV == "CS2_Positive_CS1_Negative"], nsmall = 2)`, SD = `r format(results_exp_1_h2$summary_stats$sd[results_exp_1_h2$summary_stats$IV == "CS2_Positive_CS1_Negative"], nsmall = 2)`), `r results_exp_1_h2$t_test_output`, BF10 = `r format(results_exp_1_h2$bf10, nsmall = 2)`.

#### Robustness tests

```{r}

full_sample_p_value_exp_1_h2 <- results_exp_1_h2$t_test_p

# re run tests with desired subsets of participants
results_exp_1_h2_contingency_memory <- tidied_data_exp_1 %>%
  #filter(contingency_memory == TRUE) %>%
  mutate(DV = EC_Effect_CS1_CS2_Difference_Score,
         IV = Color_Matching) %>%
  t_test_analyses(.)

results_exp_1_h2_demand_compliance <- tidied_data_exp_1 %>%
  #filter(demand_compliance == FALSE) %>%
  mutate(DV = EC_Effect_CS1_CS2_Difference_Score,
         IV = Color_Matching) %>%
  t_test_analyses(.)

results_exp_1_h2_hypothesis_aware <- tidied_data_exp_1 %>%
  #filter(hypothesis_aware == FALSE) %>%
  mutate(DV = EC_Effect_CS1_CS2_Difference_Score,
         IV = Color_Matching) %>%
  t_test_analyses(.)

results_exp_1_h2_influence_aware <- tidied_data_exp_1 %>%
  #filter(influence_aware == FALSE) %>%
  mutate(DV = EC_Effect_CS1_CS2_Difference_Score,
         IV = Color_Matching) %>%
  t_test_analyses(.)

# robustness strings
robustness_contingency_memory <- 
  ifelse((results_exp_1_h2_contingency_memory$t_test_p < 0.05 & 
            full_sample_p_value_exp_1_h2 < 0.05) |
           (results_exp_1_h2_contingency_memory$t_test_p >= 0.05 & 
              full_sample_p_value_exp_1_h2 >= 0.05), "were", "were not")

robustness_demand_compliance <- 
  ifelse((results_exp_1_h2_demand_compliance$t_test_p < 0.05 & 
            full_sample_p_value_exp_1_h2 < 0.05) |
           (results_exp_1_h2_demand_compliance$t_test_p >= 0.05 & 
              full_sample_p_value_exp_1_h2 >= 0.05), "were", "were not")

robustness_hypothesis_aware <- 
  ifelse((results_exp_1_h2_hypothesis_aware$t_test_p < 0.05 & 
            full_sample_p_value_exp_1_h2 < 0.05) |
           (results_exp_1_h2_hypothesis_aware$t_test_p >= 0.05 & 
              full_sample_p_value_exp_1_h2 >= 0.05), "were", "were not")

robustness_influence_aware <- 
  ifelse((results_exp_1_h2_influence_aware$t_test_p < 0.05 & 
            full_sample_p_value_exp_1_h2 < 0.05) |
           (results_exp_1_h2_influence_aware$t_test_p >= 0.05 & 
              full_sample_p_value_exp_1_h2 >= 0.05), "were", "were not")

```

- Results `r robustness_contingency_memory` robust to including only participants who were contingency aware, p in subsample `r apa_p_value(results_exp_1_h1_contingency_memory$t_test_p)`.
- Results `r robustness_demand_compliance` robust to including only participants who were not demand compliant, p in subsample `r apa_p_value(results_exp_1_h1_demand_compliance$t_test_p)`.
- Results `r robustness_hypothesis_aware` robust to including only participants who were not hypothesis aware, p in subsample `r apa_p_value(results_exp_1_h1_hypothesis_aware$t_test_p)`.
- Results `r robustness_influence_aware` robust to including only participants who were not influence aware, p in subsample `r apa_p_value(results_exp_1_h1_influence_aware$t_test_p)`.

### H3: Behavioural intentions

```{r echo=TRUE, results='hide'}

# set reference level to "Morag"
data_for_analysis <- tidied_data_exp_1 
data_for_analysis$intention <- relevel(data_for_analysis$intention, ref = "Morag")

results_exp_1_h3 <- multinominal_analysis(data_for_analysis)

```

Data from the behavioural intentions question were entered into a multinomial logistic regression with CSI as the reference category. Only results from the CS1-CS2 comparison are relevant to the hypothesis and will be reported here. Results demonstrated that participants responses of CS1 relative to CS2 differed between the two conditions, congruent with training, OR = `r format(results_exp_1_h3$OR[results_exp_1_h3$var == "Struan"], nsmall = 2)`, 95% CI = [`r format(results_exp_1_h3$OR_ci_lwr[results_exp_1_h3$var == "Struan"], nsmall = 2)`, `r format(results_exp_1_h3$OR_ci_upr[results_exp_1_h3$var == "Struan"], nsmall = 2)`], p `r results_exp_1_h3$p[results_exp_1_h3$var == "Struan"]`.

#### Robustness tests

```{r echo=TRUE, results='hide'}

full_sample_p_value_exp_1_h3 <- results_exp_1_h3$p[results_exp_1_h3$var == "Struan"]

# re run tests with desired subsets of participants
results_exp_1_h3_contingency_memory <- data_for_analysis %>%
  #filter(contingency_memory == TRUE) %>%
  multinominal_analysis(.)

results_exp_1_h3_demand_compliance <- data_for_analysis %>%
  #filter(demand_compliance == FALSE) %>%
  multinominal_analysis(.)

results_exp_1_h3_hypothesis_aware <- data_for_analysis %>%
  #filter(hypothesis_aware == FALSE) %>%
  multinominal_analysis(.)

results_exp_1_h3_influence_aware <- data_for_analysis %>%
  #filter(influence_aware == FALSE) %>%
  multinominal_analysis(.)

# robustness strings
robustness_contingency_memory <-
  ifelse((results_exp_1_h3_contingency_memory$p[results_exp_1_h3$var == "Struan"] < 0.05 & 
            full_sample_p_value_exp_1_h3 < 0.05) |
           (results_exp_1_h3_contingency_memory$p[results_exp_1_h3$var == "Struan"] >= 0.05 & 
              full_sample_p_value_exp_1_h3 >= 0.05), "were", "were not")

robustness_demand_compliance <-
  ifelse((results_exp_1_h3_demand_compliance$p[results_exp_1_h3$var == "Struan"] < 0.05 & 
            full_sample_p_value_exp_1_h3 < 0.05) |
           (results_exp_1_h3_demand_compliance$p[results_exp_1_h3$var == "Struan"] >= 0.05 & 
              full_sample_p_value_exp_1_h3 >= 0.05), "were", "were not")

robustness_hypothesis_aware <- 
  ifelse((results_exp_1_h3_hypothesis_aware$p[results_exp_1_h3$var == "Struan"] < 0.05 & 
            full_sample_p_value_exp_1_h3 < 0.05) |
           (results_exp_1_h3_hypothesis_aware$p[results_exp_1_h3$var == "Struan"] >= 0.05 & 
              full_sample_p_value_exp_1_h3 >= 0.05), "were", "were not")

robustness_influence_aware <- 
  ifelse((results_exp_1_h3_influence_aware$p[results_exp_1_h3$var == "Struan"] < 0.05 & 
            full_sample_p_value_exp_1_h3 < 0.05) |
           (results_exp_1_h3_influence_aware$p[results_exp_1_h3$var == "Struan"] >= 0.05 & 
              full_sample_p_value_exp_1_h3 >= 0.05), "were", "were not")

```

- Results `r robustness_contingency_memory` robust to including only participants who were contingency aware, p in subsample `r results_exp_1_h3_contingency_memory$p[results_exp_1_h3_contingency_memory$var == "Struan"]`.
- Results `r robustness_demand_compliance` robust to including only participants who were not demand compliant, p in subsample `r results_exp_1_h3_demand_compliance$p[results_exp_1_h3_demand_compliance$var == "Struan"]`.
- Results `r robustness_hypothesis_aware` robust to including only participants who were not hypothesis aware, p in subsample 
`r results_exp_1_h3_hypothesis_aware$p[results_exp_1_h3_hypothesis_aware$var == "Struan"]`.
- Results `r robustness_influence_aware` robust to including only participants who were not influence aware, p in subsample `r results_exp_1_h3_influence_aware$p[results_exp_1_h3_influence_aware$var == "Struan"]`.

## Experiment 2

### H1: IAT

```{r}

results_exp_2_h1 <- tidied_data_exp_2 %>%
  mutate(DV = IAT_Score,
         IV = Color_Matching) %>%
  t_test_analyses(.)

```

When CS2 eventually shared a color with positive words and CS1 shared a color with negative words, participants showed an automatic relative preference for CS2 over CS1 on the IAT (M = `r format(results_exp_2_h1$summary_stats$mean[results_exp_2_h1$summary_stats$IV == "CS1_Positive_CS2_Negative"], nsmall = 2)`, SD = `r format(results_exp_2_h1$summary_stats$sd[results_exp_2_h1$summary_stats$IV == "CS1_Positive_CS2_Negative"], nsmall = 2)`). whereas when CS2 eventually shared a color with negative words and CS1 shared a color with positive words, they demonstrated a relative preference for CS1 over CS2 (M = `r format(results_exp_2_h1$summary_stats$mean[results_exp_2_h1$summary_stats$IV == "CS2_Positive_CS1_Negative"], nsmall = 2)`, SD = `r format(results_exp_2_h1$summary_stats$sd[results_exp_2_h1$summary_stats$IV == "CS2_Positive_CS1_Negative"], nsmall = 2)`), `r results_exp_2_h1$t_test_output`, BF10 = `r format(results_exp_2_h1$bf10, nsmall = 2)`.

Note that this result is in the opposite direction to all other experiments.

#### Robustness tests

```{r}

full_sample_p_value_exp_2_h1 <- results_exp_2_h1$t_test_p

# re run tests with desired subsets of participants
results_exp_2_h1_contingency_memory <- tidied_data_exp_2 %>%
  #filter(contingency_memory == TRUE) %>%
  mutate(DV = IAT_Score,
         IV = Color_Matching) %>%
  t_test_analyses(.)

results_exp_2_h1_demand_compliance <- tidied_data_exp_2 %>%
  #filter(demand_compliance == FALSE) %>%
  mutate(DV = IAT_Score,
         IV = Color_Matching) %>%
  t_test_analyses(.)

results_exp_2_h1_hypothesis_aware <- tidied_data_exp_2 %>%
  #filter(hypothesis_aware == FALSE) %>%
  mutate(DV = IAT_Score,
         IV = Color_Matching) %>%
  t_test_analyses(.)

results_exp_2_h1_influence_aware <- tidied_data_exp_2 %>%
  #filter(influence_aware == FALSE) %>%
  mutate(DV = IAT_Score,
         IV = Color_Matching) %>%
  t_test_analyses(.)

# robustness strings
robustness_contingency_memory <- 
  ifelse((results_exp_2_h1_contingency_memory$t_test_p < 0.05 & 
            full_sample_p_value_exp_2_h1 < 0.05) |
           (results_exp_2_h1_contingency_memory$t_test_p >= 0.05 & 
              full_sample_p_value_exp_2_h1 >= 0.05), "were", "were not")

robustness_demand_compliance <- 
  ifelse((results_exp_2_h1_demand_compliance$t_test_p < 0.05 & 
            full_sample_p_value_exp_2_h1 < 0.05) |
           (results_exp_2_h1_demand_compliance$t_test_p >= 0.05 & 
              full_sample_p_value_exp_2_h1 >= 0.05), "were", "were not")

robustness_hypothesis_aware <- 
  ifelse((results_exp_2_h1_hypothesis_aware$t_test_p < 0.05 & 
            full_sample_p_value_exp_2_h1 < 0.05) |
           (results_exp_2_h1_hypothesis_aware$t_test_p >= 0.05 & 
              full_sample_p_value_exp_2_h1 >= 0.05), "were", "were not")

robustness_influence_aware <- 
  ifelse((results_exp_2_h1_influence_aware$t_test_p < 0.05 & 
            full_sample_p_value_exp_2_h1 < 0.05) |
           (results_exp_2_h1_influence_aware$t_test_p >= 0.05 & 
              full_sample_p_value_exp_2_h1 >= 0.05), "were", "were not")

```

- Results `r robustness_contingency_memory` robust to including only participants who were contingency aware, p in subsample `r apa_p_value(results_exp_2_h1_contingency_memory$t_test_p)`.
- Results `r robustness_demand_compliance` robust to including only participants who were not demand compliant, p in subsample `r apa_p_value(results_exp_2_h1_demand_compliance$t_test_p)`.
- Results `r robustness_hypothesis_aware` robust to including only participants who were not hypothesis aware, p in subsample `r apa_p_value(results_exp_2_h1_hypothesis_aware$t_test_p)`.
- Results `r robustness_influence_aware` robust to including only participants who were not influence aware, p in subsample `r apa_p_value(results_exp_2_h1_influence_aware$t_test_p)`.

### H2: Self-report ratings

```{r}

results_exp_2_h2 <- tidied_data_exp_2 %>%
  mutate(DV = EC_Effect_CS1_CS2_Difference_Score,
         IV = Color_Matching) %>%
  t_test_analyses(.)

```

Regardless of whether CS1 eventually shared a color with positive or negative words, participants showed a relative preference on the self-report ratings for CS2 over CS1 (CS1-positive condition: M = `r format(results_exp_2_h2$summary_stats$mean[results_exp_2_h2$summary_stats$IV == "CS1_Positive_CS2_Negative"], nsmall = 2)`, SD = `r format(results_exp_2_h2$summary_stats$sd[results_exp_2_h2$summary_stats$IV == "CS1_Positive_CS2_Negative"], nsmall = 2)`; CS1-negative condition: M = `r format(results_exp_2_h2$summary_stats$mean[results_exp_2_h2$summary_stats$IV == "CS2_Positive_CS1_Negative"], nsmall = 2)`, SD = `r format(results_exp_2_h2$summary_stats$sd[results_exp_2_h2$summary_stats$IV == "CS2_Positive_CS1_Negative"], nsmall = 2)`), `r results_exp_2_h2$t_test_output`, BF10 = `r format(results_exp_2_h2$bf10, nsmall = 2)`.

Note that this null result is different to all other experiments.

#### Robustness tests

```{r}

full_sample_p_value_exp_2_h2 <- results_exp_2_h2$t_test_p

# re run tests with desired subsets of participants
results_exp_2_h2_contingency_memory <- tidied_data_exp_2 %>%
  #filter(contingency_memory == TRUE) %>%
  mutate(DV = EC_Effect_CS1_CS2_Difference_Score,
         IV = Color_Matching) %>%
  t_test_analyses(.)

results_exp_2_h2_demand_compliance <- tidied_data_exp_2 %>%
  #filter(demand_compliance == FALSE) %>%
  mutate(DV = EC_Effect_CS1_CS2_Difference_Score,
         IV = Color_Matching) %>%
  t_test_analyses(.)

results_exp_2_h2_hypothesis_aware <- tidied_data_exp_2 %>%
  #filter(hypothesis_aware == FALSE) %>%
  mutate(DV = EC_Effect_CS1_CS2_Difference_Score,
         IV = Color_Matching) %>%
  t_test_analyses(.)

results_exp_2_h2_influence_aware <- tidied_data_exp_2 %>%
  #filter(influence_aware == FALSE) %>%
  mutate(DV = EC_Effect_CS1_CS2_Difference_Score,
         IV = Color_Matching) %>%
  t_test_analyses(.)

# robustness strings
robustness_contingency_memory <- 
  ifelse((results_exp_2_h2_contingency_memory$t_test_p < 0.05 & 
            full_sample_p_value_exp_2_h2 < 0.05) |
           (results_exp_2_h2_contingency_memory$t_test_p >= 0.05 & 
              full_sample_p_value_exp_2_h2 >= 0.05), "were", "were not")

robustness_demand_compliance <- 
  ifelse((results_exp_2_h2_demand_compliance$t_test_p < 0.05 & 
            full_sample_p_value_exp_2_h2 < 0.05) |
           (results_exp_2_h2_demand_compliance$t_test_p >= 0.05 & 
              full_sample_p_value_exp_2_h2 >= 0.05), "were", "were not")

robustness_hypothesis_aware <- 
  ifelse((results_exp_2_h2_hypothesis_aware$t_test_p < 0.05 & 
            full_sample_p_value_exp_2_h2 < 0.05) |
           (results_exp_2_h2_hypothesis_aware$t_test_p >= 0.05 & 
              full_sample_p_value_exp_2_h2 >= 0.05), "were", "were not")

robustness_influence_aware <- 
  ifelse((results_exp_2_h2_influence_aware$t_test_p < 0.05 & 
            full_sample_p_value_exp_2_h2 < 0.05) |
           (results_exp_2_h2_influence_aware$t_test_p >= 0.05 & 
              full_sample_p_value_exp_2_h2 >= 0.05), "were", "were not")

```

- Results `r robustness_contingency_memory` robust to including only participants who were contingency aware, p in subsample `r apa_p_value(results_exp_2_h2_contingency_memory$t_test_p)`.
- Results `r robustness_demand_compliance` robust to including only participants who were not demand compliant, p in subsample `r apa_p_value(results_exp_2_h2_demand_compliance$t_test_p)`.
- Results `r robustness_hypothesis_aware` robust to including only participants who were not hypothesis aware, p in subsample `r apa_p_value(results_exp_2_h2_hypothesis_aware$t_test_p)`.
- Results `r robustness_influence_aware` robust to including only participants who were not influence aware, p in subsample `r apa_p_value(results_exp_2_h2_influence_aware$t_test_p)`.

### H3: Behavioural intentions

```{r echo=TRUE, results='hide'}

# set reference level to "Morag"
data_for_analysis <- tidied_data_exp_2 
data_for_analysis$intention <- relevel(data_for_analysis$intention, ref = "Morag")

results_exp_2_h3 <- multinominal_analysis(data_for_analysis)

```

Data from the behavioural intentions question were entered into a multinomial logistic regression with CSI as the reference category. Only results from the CS1-CS2 comparison are relevant to the hypothesis and will be reported here. Results demonstrated that participants responses of CS1 relative to CS2 differed between the two conditions, but in the opposite direction to that predicted, OR = `r format(results_exp_2_h3$OR[results_exp_2_h3$var == "Struan"], nsmall = 2)`, 95% CI = [`r format(results_exp_2_h3$OR_ci_lwr[results_exp_2_h3$var == "Struan"], nsmall = 2)`, `r format(results_exp_2_h3$OR_ci_upr[results_exp_2_h3$var == "Struan"], nsmall = 2)`], p `r results_exp_2_h3$p[results_exp_2_h3$var == "Struan"]`.

Note that this result is in the opposite direction to all other experiments.

#### Robustness tests

```{r echo=TRUE, results='hide'}

full_sample_p_value_exp_2_h3 <- results_exp_2_h3$p[results_exp_2_h3$var == "Struan"]

# re run tests with desired subsets of participants
results_exp_2_h3_contingency_memory <- data_for_analysis %>%
  #filter(contingency_memory == TRUE) %>%
  multinominal_analysis(.)

results_exp_2_h3_demand_compliance <- data_for_analysis %>%
  #filter(demand_compliance == FALSE) %>%
  multinominal_analysis(.)

results_exp_2_h3_hypothesis_aware <- data_for_analysis %>%
  #filter(hypothesis_aware == FALSE) %>%
  multinominal_analysis(.)

results_exp_2_h3_influence_aware <- data_for_analysis %>%
  #filter(influence_aware == FALSE) %>%
  multinominal_analysis(.)

# robustness strings
robustness_contingency_memory <-
  ifelse((results_exp_2_h3_contingency_memory$p[results_exp_2_h3$var == "Struan"] < 0.05 & 
            full_sample_p_value_exp_2_h3 < 0.05) |
           (results_exp_2_h3_contingency_memory$p[results_exp_2_h3$var == "Struan"] >= 0.05 & 
              full_sample_p_value_exp_2_h3 >= 0.05), "were", "were not")

robustness_demand_compliance <-
  ifelse((results_exp_2_h3_demand_compliance$p[results_exp_2_h3$var == "Struan"] < 0.05 & 
            full_sample_p_value_exp_2_h3 < 0.05) |
           (results_exp_2_h3_demand_compliance$p[results_exp_2_h3$var == "Struan"] >= 0.05 & 
              full_sample_p_value_exp_2_h3 >= 0.05), "were", "were not")

robustness_hypothesis_aware <- 
  ifelse((results_exp_2_h3_hypothesis_aware$p[results_exp_2_h3$var == "Struan"] < 0.05 & 
            full_sample_p_value_exp_2_h3 < 0.05) |
           (results_exp_2_h3_hypothesis_aware$p[results_exp_2_h3$var == "Struan"] >= 0.05 & 
              full_sample_p_value_exp_2_h3 >= 0.05), "were", "were not")

robustness_influence_aware <- 
  ifelse((results_exp_2_h3_influence_aware$p[results_exp_2_h3$var == "Struan"] < 0.05 & 
            full_sample_p_value_exp_2_h3 < 0.05) |
           (results_exp_2_h3_influence_aware$p[results_exp_2_h3$var == "Struan"] >= 0.05 & 
              full_sample_p_value_exp_2_h3 >= 0.05), "were", "were not")

```

- Results `r robustness_contingency_memory` robust to including only participants who were contingency aware, p in subsample `r results_exp_2_h3_contingency_memory$p[results_exp_2_h3_contingency_memory$var == "Struan"]`.
- Results `r robustness_demand_compliance` robust to including only participants who were not demand compliant, p in subsample `r results_exp_2_h3_demand_compliance$p[results_exp_2_h3_demand_compliance$var == "Struan"]`.
- Results `r robustness_hypothesis_aware` robust to including only participants who were not hypothesis aware, p in subsample 
`r results_exp_2_h3_hypothesis_aware$p[results_exp_2_h3_hypothesis_aware$var == "Struan"]`.
- Results `r robustness_influence_aware` robust to including only participants who were not influence aware, p in subsample `r results_exp_2_h3_influence_aware$p[results_exp_2_h3_influence_aware$var == "Struan"]`.

## Experiment 3

### H1: IAT

```{r}

results_exp_3_h1 <- tidied_data_exp_3 %>%
  mutate(DV = IAT_Score,
         IV = Color_Matching) %>%
  t_test_analyses(.)

```

When CS1 eventually shared a color with positive words and CS2 shared a color with negative words, participants showed an automatic relative preference for CS1 over CS2 on the IAT (M = `r format(results_exp_3_h1$summary_stats$mean[results_exp_3_h1$summary_stats$IV == "CS1_Positive_CS2_Negative"], nsmall = 2)`, SD = `r format(results_exp_3_h1$summary_stats$sd[results_exp_3_h1$summary_stats$IV == "CS1_Positive_CS2_Negative"], nsmall = 2)`), whereas when CS1 eventually shared a color with negative words and CS2 shared a color with positive words, they demonstrated a relative preference for CS2 over CS1 (M = `r format(results_exp_3_h1$summary_stats$mean[results_exp_3_h1$summary_stats$IV == "CS2_Positive_CS1_Negative"], nsmall = 2)`, SD = `r format(results_exp_3_h1$summary_stats$sd[results_exp_3_h1$summary_stats$IV == "CS2_Positive_CS1_Negative"], nsmall = 2)`), `r results_exp_3_h1$t_test_output`, BF10 = `r format(results_exp_3_h1$bf10, nsmall = 2)`.

#### Robustness tests

```{r}

full_sample_p_value_exp_3_h1 <- results_exp_3_h1$t_test_p

# re run tests with desired subsets of participants
results_exp_3_h1_contingency_memory <- tidied_data_exp_3 %>%
  #filter(contingency_memory == TRUE) %>%
  mutate(DV = IAT_Score,
         IV = Color_Matching) %>%
  t_test_analyses(.)

results_exp_3_h1_demand_compliance <- tidied_data_exp_3 %>%
  #filter(demand_compliance == FALSE) %>%
  mutate(DV = IAT_Score,
         IV = Color_Matching) %>%
  t_test_analyses(.)

results_exp_3_h1_hypothesis_aware <- tidied_data_exp_3 %>%
  #filter(hypothesis_aware == FALSE) %>%
  mutate(DV = IAT_Score,
         IV = Color_Matching) %>%
  t_test_analyses(.)

results_exp_3_h1_influence_aware <- tidied_data_exp_3 %>%
  #filter(influence_aware == FALSE) %>%
  mutate(DV = IAT_Score,
         IV = Color_Matching) %>%
  t_test_analyses(.)

# robustness strings
robustness_contingency_memory <- 
  ifelse((results_exp_3_h1_contingency_memory$t_test_p < 0.05 & 
            full_sample_p_value_exp_3_h1 < 0.05) |
           (results_exp_3_h1_contingency_memory$t_test_p >= 0.05 & 
              full_sample_p_value_exp_3_h1 >= 0.05), "were", "were not")

robustness_demand_compliance <- 
  ifelse((results_exp_3_h1_demand_compliance$t_test_p < 0.05 & 
            full_sample_p_value_exp_3_h1 < 0.05) |
           (results_exp_3_h1_demand_compliance$t_test_p >= 0.05 & 
              full_sample_p_value_exp_3_h1 >= 0.05), "were", "were not")

robustness_hypothesis_aware <- 
  ifelse((results_exp_3_h1_hypothesis_aware$t_test_p < 0.05 & 
            full_sample_p_value_exp_3_h1 < 0.05) |
           (results_exp_3_h1_hypothesis_aware$t_test_p >= 0.05 & 
              full_sample_p_value_exp_3_h1 >= 0.05), "were", "were not")

robustness_influence_aware <- 
  ifelse((results_exp_3_h1_influence_aware$t_test_p < 0.05 & 
            full_sample_p_value_exp_3_h1 < 0.05) |
           (results_exp_3_h1_influence_aware$t_test_p >= 0.05 & 
              full_sample_p_value_exp_3_h1 >= 0.05), "were", "were not")

```

- Results `r robustness_contingency_memory` robust to including only participants who were contingency aware, p in subsample `r apa_p_value(results_exp_3_h1_contingency_memory$t_test_p)`.
- Results `r robustness_demand_compliance` robust to including only participants who were not demand compliant, p in subsample `r apa_p_value(results_exp_3_h1_demand_compliance$t_test_p)`.
- Results `r robustness_hypothesis_aware` robust to including only participants who were not hypothesis aware, p in subsample `r apa_p_value(results_exp_3_h1_hypothesis_aware$t_test_p)`.
- Results `r robustness_influence_aware` robust to including only participants who were not influence aware, p in subsample `r apa_p_value(results_exp_3_h1_influence_aware$t_test_p)`.

### H2: Self-report ratings

```{r}

results_exp_3_h2 <- tidied_data_exp_3 %>%
  mutate(DV = EC_Effect_CS1_CS2_Difference_Score,
         IV = Color_Matching) %>%
  t_test_analyses(.)

```

When CS1 eventually shared a color with positive words and CS2 shared a color with negative words, participants showed a relative preference on the self-report ratings for CS1 over CS2 (M = `r format(results_exp_3_h2$summary_stats$mean[results_exp_3_h2$summary_stats$IV == "CS1_Positive_CS2_Negative"], nsmall = 2)`, SD = `r format(results_exp_3_h2$summary_stats$sd[results_exp_3_h2$summary_stats$IV == "CS1_Positive_CS2_Negative"], nsmall = 2)`), whereas when CS1 eventually shared a color with negative words and CS2 shared a color with positive words, they demonstrated a relative preference for CS2 over CS1 (M = `r format(results_exp_3_h2$summary_stats$mean[results_exp_3_h2$summary_stats$IV == "CS2_Positive_CS1_Negative"], nsmall = 2)`, SD = `r format(results_exp_3_h2$summary_stats$sd[results_exp_3_h2$summary_stats$IV == "CS2_Positive_CS1_Negative"], nsmall = 2)`), `r results_exp_3_h2$t_test_output`, BF10 = `r format(results_exp_3_h2$bf10, nsmall = 2)`.

#### Robustness tests

```{r}

full_sample_p_value_exp_3_h2 <- results_exp_3_h2$t_test_p

# re run tests with desired subsets of participants
results_exp_3_h2_contingency_memory <- tidied_data_exp_3 %>%
  #filter(contingency_memory == TRUE) %>%
  mutate(DV = EC_Effect_CS1_CS2_Difference_Score,
         IV = Color_Matching) %>%
  t_test_analyses(.)

results_exp_3_h2_demand_compliance <- tidied_data_exp_3 %>%
  #filter(demand_compliance == FALSE) %>%
  mutate(DV = EC_Effect_CS1_CS2_Difference_Score,
         IV = Color_Matching) %>%
  t_test_analyses(.)

results_exp_3_h2_hypothesis_aware <- tidied_data_exp_3 %>%
  #filter(hypothesis_aware == FALSE) %>%
  mutate(DV = EC_Effect_CS1_CS2_Difference_Score,
         IV = Color_Matching) %>%
  t_test_analyses(.)

results_exp_3_h2_influence_aware <- tidied_data_exp_3 %>%
  #filter(influence_aware == FALSE) %>%
  mutate(DV = EC_Effect_CS1_CS2_Difference_Score,
         IV = Color_Matching) %>%
  t_test_analyses(.)

# robustness strings
robustness_contingency_memory <- 
  ifelse((results_exp_3_h2_contingency_memory$t_test_p < 0.05 & 
            full_sample_p_value_exp_3_h2 < 0.05) |
           (results_exp_3_h2_contingency_memory$t_test_p >= 0.05 & 
              full_sample_p_value_exp_3_h2 >= 0.05), "were", "were not")

robustness_demand_compliance <- 
  ifelse((results_exp_3_h2_demand_compliance$t_test_p < 0.05 & 
            full_sample_p_value_exp_3_h2 < 0.05) |
           (results_exp_3_h2_demand_compliance$t_test_p >= 0.05 & 
              full_sample_p_value_exp_3_h2 >= 0.05), "were", "were not")

robustness_hypothesis_aware <- 
  ifelse((results_exp_3_h2_hypothesis_aware$t_test_p < 0.05 & 
            full_sample_p_value_exp_3_h2 < 0.05) |
           (results_exp_3_h2_hypothesis_aware$t_test_p >= 0.05 & 
              full_sample_p_value_exp_3_h2 >= 0.05), "were", "were not")

robustness_influence_aware <- 
  ifelse((results_exp_3_h2_influence_aware$t_test_p < 0.05 & 
            full_sample_p_value_exp_3_h2 < 0.05) |
           (results_exp_3_h2_influence_aware$t_test_p >= 0.05 & 
              full_sample_p_value_exp_3_h2 >= 0.05), "were", "were not")

```

- Results `r robustness_contingency_memory` robust to including only participants who were contingency aware, p in subsample `r apa_p_value(results_exp_3_h2_contingency_memory$t_test_p)`.
- Results `r robustness_demand_compliance` robust to including only participants who were not demand compliant, p in subsample `r apa_p_value(results_exp_3_h2_demand_compliance$t_test_p)`.
- Results `r robustness_hypothesis_aware` robust to including only participants who were not hypothesis aware, p in subsample `r apa_p_value(results_exp_3_h2_hypothesis_aware$t_test_p)`.
- Results `r robustness_influence_aware` robust to including only participants who were not influence aware, p in subsample `r apa_p_value(results_exp_3_h2_influence_aware$t_test_p)`.

### H3: Behavioural intentions

```{r echo=TRUE, results='hide'}

# set reference level to "Morag"
data_for_analysis <- tidied_data_exp_3 
data_for_analysis$intention <- relevel(data_for_analysis$intention, ref = "Morag")

results_exp_3_h3 <- multinominal_analysis(data_for_analysis)

```

Data from the behavioural intentions question were entered into a multinomial logistic regression with CSI as the reference category. Only results from the CS1-CS2 comparison are relevant to the hypothesis and will be reported here. Results demonstrated that participants responses of CS1 relative to CS2 differed between the two conditions, congruent with training, OR = `r format(results_exp_3_h3$OR[results_exp_3_h3$var == "Struan"], nsmall = 2)`, 95% CI = [`r format(results_exp_3_h3$OR_ci_lwr[results_exp_3_h3$var == "Struan"], nsmall = 2)`, `r format(results_exp_3_h3$OR_ci_upr[results_exp_3_h3$var == "Struan"], nsmall = 2)`], p `r results_exp_3_h3$p[results_exp_3_h3$var == "Struan"]`.

#### Robustness tests

```{r echo=TRUE, results='hide'}

full_sample_p_value_exp_3_h3 <- results_exp_3_h3$p[results_exp_3_h3$var == "Struan"]

# re run tests with desired subsets of participants
results_exp_3_h3_contingency_memory <- data_for_analysis %>%
  #filter(contingency_memory == TRUE) %>%
  multinominal_analysis(.)

results_exp_3_h3_demand_compliance <- data_for_analysis %>%
  #filter(demand_compliance == FALSE) %>%
  multinominal_analysis(.)

results_exp_3_h3_hypothesis_aware <- data_for_analysis %>%
  #filter(hypothesis_aware == FALSE) %>%
  multinominal_analysis(.)

results_exp_3_h3_influence_aware <- data_for_analysis %>%
  #filter(influence_aware == FALSE) %>%
  multinominal_analysis(.)

# robustness strings
robustness_contingency_memory <-
  ifelse((results_exp_3_h3_contingency_memory$p[results_exp_3_h3$var == "Struan"] < 0.05 & 
            full_sample_p_value_exp_3_h3 < 0.05) |
           (results_exp_3_h3_contingency_memory$p[results_exp_3_h3$var == "Struan"] >= 0.05 & 
              full_sample_p_value_exp_3_h3 >= 0.05), "were", "were not")

robustness_demand_compliance <-
  ifelse((results_exp_3_h3_demand_compliance$p[results_exp_3_h3$var == "Struan"] < 0.05 & 
            full_sample_p_value_exp_3_h3 < 0.05) |
           (results_exp_3_h3_demand_compliance$p[results_exp_3_h3$var == "Struan"] >= 0.05 & 
              full_sample_p_value_exp_3_h3 >= 0.05), "were", "were not")

robustness_hypothesis_aware <- 
  ifelse((results_exp_3_h3_hypothesis_aware$p[results_exp_3_h3$var == "Struan"] < 0.05 & 
            full_sample_p_value_exp_3_h3 < 0.05) |
           (results_exp_3_h3_hypothesis_aware$p[results_exp_3_h3$var == "Struan"] >= 0.05 & 
              full_sample_p_value_exp_3_h3 >= 0.05), "were", "were not")

robustness_influence_aware <- 
  ifelse((results_exp_3_h3_influence_aware$p[results_exp_3_h3$var == "Struan"] < 0.05 & 
            full_sample_p_value_exp_3_h3 < 0.05) |
           (results_exp_3_h3_influence_aware$p[results_exp_3_h3$var == "Struan"] >= 0.05 & 
              full_sample_p_value_exp_3_h3 >= 0.05), "were", "were not")

```

- Results `r robustness_contingency_memory` robust to including only participants who were contingency aware, p in subsample `r results_exp_3_h3_contingency_memory$p[results_exp_3_h3_contingency_memory$var == "Struan"]`.
- Results `r robustness_demand_compliance` robust to including only participants who were not demand compliant, p in subsample `r results_exp_3_h3_demand_compliance$p[results_exp_3_h3_demand_compliance$var == "Struan"]`.
- Results `r robustness_hypothesis_aware` robust to including only participants who were not hypothesis aware, p in subsample 
`r results_exp_3_h3_hypothesis_aware$p[results_exp_3_h3_hypothesis_aware$var == "Struan"]`.
- Results `r robustness_influence_aware` robust to including only participants who were not influence aware, p in subsample `r results_exp_3_h3_influence_aware$p[results_exp_3_h3_influence_aware$var == "Struan"]`.

## Experiment 4

### H1: IAT

```{r}

results_exp_4_h1 <- tidied_data_exp_4 %>%
  mutate(DV = IAT_Score,
         IV = Color_Matching) %>%
  t_test_analyses(.)

```

When CS1 eventually shared a color with positive words and CS2 shared a color with negative words, participants showed an automatic relative preference for CS1 over CS2 on the IAT (M = `r format(results_exp_4_h1$summary_stats$mean[results_exp_4_h1$summary_stats$IV == "CS1_Positive_CS2_Negative"], nsmall = 2)`, SD = `r format(results_exp_4_h1$summary_stats$sd[results_exp_4_h1$summary_stats$IV == "CS1_Positive_CS2_Negative"], nsmall = 2)`), whereas when CS1 eventually shared a color with negative words and CS2 shared a color with positive words, they demonstrated a relative preference for CS2 over CS1 (M = `r format(results_exp_4_h1$summary_stats$mean[results_exp_4_h1$summary_stats$IV == "CS2_Positive_CS1_Negative"], nsmall = 2)`, SD = `r format(results_exp_4_h1$summary_stats$sd[results_exp_4_h1$summary_stats$IV == "CS2_Positive_CS1_Negative"], nsmall = 2)`), `r results_exp_4_h1$t_test_output`, BF10 = `r format(results_exp_4_h1$bf10, nsmall = 2)`.

#### Robustness tests

```{r}

full_sample_p_value_exp_4_h1 <- results_exp_4_h1$t_test_p

# re run tests with desired subsets of participants
results_exp_4_h1_contingency_memory <- tidied_data_exp_4 %>%
  #filter(contingency_memory == TRUE) %>%
  mutate(DV = IAT_Score,
         IV = Color_Matching) %>%
  t_test_analyses(.)

results_exp_4_h1_demand_compliance <- tidied_data_exp_4 %>%
  #filter(demand_compliance == FALSE) %>%
  mutate(DV = IAT_Score,
         IV = Color_Matching) %>%
  t_test_analyses(.)

results_exp_4_h1_hypothesis_aware <- tidied_data_exp_4 %>%
  #filter(hypothesis_aware == FALSE) %>%
  mutate(DV = IAT_Score,
         IV = Color_Matching) %>%
  t_test_analyses(.)

results_exp_4_h1_influence_aware <- tidied_data_exp_4 %>%
  #filter(influence_aware == FALSE) %>%
  mutate(DV = IAT_Score,
         IV = Color_Matching) %>%
  t_test_analyses(.)

# robustness strings
robustness_contingency_memory <- 
  ifelse((results_exp_4_h1_contingency_memory$t_test_p < 0.05 & 
            full_sample_p_value_exp_4_h1 < 0.05) |
           (results_exp_4_h1_contingency_memory$t_test_p >= 0.05 & 
              full_sample_p_value_exp_4_h1 >= 0.05), "were", "were not")

robustness_demand_compliance <- 
  ifelse((results_exp_4_h1_demand_compliance$t_test_p < 0.05 & 
            full_sample_p_value_exp_4_h1 < 0.05) |
           (results_exp_4_h1_demand_compliance$t_test_p >= 0.05 & 
              full_sample_p_value_exp_4_h1 >= 0.05), "were", "were not")

robustness_hypothesis_aware <- 
  ifelse((results_exp_4_h1_hypothesis_aware$t_test_p < 0.05 & 
            full_sample_p_value_exp_4_h1 < 0.05) |
           (results_exp_4_h1_hypothesis_aware$t_test_p >= 0.05 & 
              full_sample_p_value_exp_4_h1 >= 0.05), "were", "were not")

robustness_influence_aware <- 
  ifelse((results_exp_4_h1_influence_aware$t_test_p < 0.05 & 
            full_sample_p_value_exp_4_h1 < 0.05) |
           (results_exp_4_h1_influence_aware$t_test_p >= 0.05 & 
              full_sample_p_value_exp_4_h1 >= 0.05), "were", "were not")

```

- Results `r robustness_contingency_memory` robust to including only participants who were contingency aware, p in subsample `r apa_p_value(results_exp_4_h1_contingency_memory$t_test_p)`.
- Results `r robustness_demand_compliance` robust to including only participants who were not demand compliant, p in subsample `r apa_p_value(results_exp_4_h1_demand_compliance$t_test_p)`.
- Results `r robustness_hypothesis_aware` robust to including only participants who were not hypothesis aware, p in subsample `r apa_p_value(results_exp_4_h1_hypothesis_aware$t_test_p)`.
- Results `r robustness_influence_aware` robust to including only participants who were not influence aware, p in subsample `r apa_p_value(results_exp_4_h1_influence_aware$t_test_p)`.

### H2: Self-report ratings

```{r}

results_exp_4_h2 <- tidied_data_exp_4 %>%
  mutate(DV = EC_Effect_CS1_CS2_Difference_Score,
         IV = Color_Matching) %>%
  t_test_analyses(.)

```

When CS1 eventually shared a color with positive words and CS2 shared a color with negative words, participants showed a relative preference on the self-report ratings for CS1 over CS2 (M = `r format(results_exp_4_h2$summary_stats$mean[results_exp_4_h2$summary_stats$IV == "CS1_Positive_CS2_Negative"], nsmall = 2)`, SD = `r format(results_exp_4_h2$summary_stats$sd[results_exp_4_h2$summary_stats$IV == "CS1_Positive_CS2_Negative"], nsmall = 2)`), whereas when CS1 eventually shared a color with negative words and CS2 shared a color with positive words, they demonstrated a relative preference for CS2 over CS1 (M = `r format(results_exp_4_h2$summary_stats$mean[results_exp_4_h2$summary_stats$IV == "CS2_Positive_CS1_Negative"], nsmall = 2)`, SD = `r format(results_exp_4_h2$summary_stats$sd[results_exp_4_h2$summary_stats$IV == "CS2_Positive_CS1_Negative"], nsmall = 2)`), `r results_exp_4_h2$t_test_output`, BF10 = `r format(results_exp_4_h2$bf10, nsmall = 2)`.

#### Robustness tests

```{r}

full_sample_p_value_exp_4_h2 <- results_exp_4_h2$t_test_p

# re run tests with desired subsets of participants
results_exp_4_h2_contingency_memory <- tidied_data_exp_4 %>%
  #filter(contingency_memory == TRUE) %>%
  mutate(DV = EC_Effect_CS1_CS2_Difference_Score,
         IV = Color_Matching) %>%
  t_test_analyses(.)

results_exp_4_h2_demand_compliance <- tidied_data_exp_4 %>%
  #filter(demand_compliance == FALSE) %>%
  mutate(DV = EC_Effect_CS1_CS2_Difference_Score,
         IV = Color_Matching) %>%
  t_test_analyses(.)

results_exp_4_h2_hypothesis_aware <- tidied_data_exp_4 %>%
  #filter(hypothesis_aware == FALSE) %>%
  mutate(DV = EC_Effect_CS1_CS2_Difference_Score,
         IV = Color_Matching) %>%
  t_test_analyses(.)

results_exp_4_h2_influence_aware <- tidied_data_exp_4 %>%
  #filter(influence_aware == FALSE) %>%
  mutate(DV = EC_Effect_CS1_CS2_Difference_Score,
         IV = Color_Matching) %>%
  t_test_analyses(.)

# robustness strings
robustness_contingency_memory <- 
  ifelse((results_exp_4_h2_contingency_memory$t_test_p < 0.05 & 
            full_sample_p_value_exp_4_h2 < 0.05) |
           (results_exp_4_h2_contingency_memory$t_test_p >= 0.05 & 
              full_sample_p_value_exp_4_h2 >= 0.05), "were", "were not")

robustness_demand_compliance <- 
  ifelse((results_exp_4_h2_demand_compliance$t_test_p < 0.05 & 
            full_sample_p_value_exp_4_h2 < 0.05) |
           (results_exp_4_h2_demand_compliance$t_test_p >= 0.05 & 
              full_sample_p_value_exp_4_h2 >= 0.05), "were", "were not")

robustness_hypothesis_aware <- 
  ifelse((results_exp_4_h2_hypothesis_aware$t_test_p < 0.05 & 
            full_sample_p_value_exp_4_h2 < 0.05) |
           (results_exp_4_h2_hypothesis_aware$t_test_p >= 0.05 & 
              full_sample_p_value_exp_4_h2 >= 0.05), "were", "were not")

robustness_influence_aware <- 
  ifelse((results_exp_4_h2_influence_aware$t_test_p < 0.05 & 
            full_sample_p_value_exp_4_h2 < 0.05) |
           (results_exp_4_h2_influence_aware$t_test_p >= 0.05 & 
              full_sample_p_value_exp_4_h2 >= 0.05), "were", "were not")

```

- Results `r robustness_contingency_memory` robust to including only participants who were contingency aware, p in subsample `r apa_p_value(results_exp_4_h2_contingency_memory$t_test_p)`.
- Results `r robustness_demand_compliance` robust to including only participants who were not demand compliant, p in subsample `r apa_p_value(results_exp_4_h2_demand_compliance$t_test_p)`.
- Results `r robustness_hypothesis_aware` robust to including only participants who were not hypothesis aware, p in subsample `r apa_p_value(results_exp_4_h2_hypothesis_aware$t_test_p)`.
- Results `r robustness_influence_aware` robust to including only participants who were not influence aware, p in subsample `r apa_p_value(results_exp_4_h2_influence_aware$t_test_p)`.

### H3: Behavioural intentions

```{r echo=TRUE, results='hide'}

# set reference level to "Morag"
data_for_analysis <- tidied_data_exp_4 
data_for_analysis$intention <- relevel(data_for_analysis$intention, ref = "Morag")

results_exp_4_h3 <- multinominal_analysis(data_for_analysis)

```

Data from the behavioural intentions question were entered into a multinomial logistic regression with CSI as the reference category. Only results from the CS1-CS2 comparison are relevant to the hypothesis and will be reported here. Results demonstrated that participants responses of CS1 relative to CS2 differed between the two conditions, congruent with training, OR = `r format(results_exp_4_h3$OR[results_exp_4_h3$var == "Struan"], nsmall = 2)`, 95% CI = [`r format(results_exp_4_h3$OR_ci_lwr[results_exp_4_h3$var == "Struan"], nsmall = 2)`, `r format(results_exp_4_h3$OR_ci_upr[results_exp_4_h3$var == "Struan"], nsmall = 2)`], p `r results_exp_4_h3$p[results_exp_4_h3$var == "Struan"]`.

#### Robustness tests

```{r echo=TRUE, results='hide'}

full_sample_p_value_exp_4_h3 <- results_exp_4_h3$p[results_exp_4_h3$var == "Struan"]

# re run tests with desired subsets of participants
results_exp_4_h3_contingency_memory <- data_for_analysis %>%
  #filter(contingency_memory == TRUE) %>%
  multinominal_analysis(.)

results_exp_4_h3_demand_compliance <- data_for_analysis %>%
  #filter(demand_compliance == FALSE) %>%
  multinominal_analysis(.)

results_exp_4_h3_hypothesis_aware <- data_for_analysis %>%
  #filter(hypothesis_aware == FALSE) %>%
  multinominal_analysis(.)

results_exp_4_h3_influence_aware <- data_for_analysis %>%
  #filter(influence_aware == FALSE) %>%
  multinominal_analysis(.)

# robustness strings
robustness_contingency_memory <-
  ifelse((results_exp_4_h3_contingency_memory$p[results_exp_4_h3$var == "Struan"] < 0.05 & 
            full_sample_p_value_exp_4_h3 < 0.05) |
           (results_exp_4_h3_contingency_memory$p[results_exp_4_h3$var == "Struan"] >= 0.05 & 
              full_sample_p_value_exp_4_h3 >= 0.05), "were", "were not")

robustness_demand_compliance <-
  ifelse((results_exp_4_h3_demand_compliance$p[results_exp_4_h3$var == "Struan"] < 0.05 & 
            full_sample_p_value_exp_4_h3 < 0.05) |
           (results_exp_4_h3_demand_compliance$p[results_exp_4_h3$var == "Struan"] >= 0.05 & 
              full_sample_p_value_exp_4_h3 >= 0.05), "were", "were not")

robustness_hypothesis_aware <- 
  ifelse((results_exp_4_h3_hypothesis_aware$p[results_exp_4_h3$var == "Struan"] < 0.05 & 
            full_sample_p_value_exp_4_h3 < 0.05) |
           (results_exp_4_h3_hypothesis_aware$p[results_exp_4_h3$var == "Struan"] >= 0.05 & 
              full_sample_p_value_exp_4_h3 >= 0.05), "were", "were not")

robustness_influence_aware <- 
  ifelse((results_exp_4_h3_influence_aware$p[results_exp_4_h3$var == "Struan"] < 0.05 & 
            full_sample_p_value_exp_4_h3 < 0.05) |
           (results_exp_4_h3_influence_aware$p[results_exp_4_h3$var == "Struan"] >= 0.05 & 
              full_sample_p_value_exp_4_h3 >= 0.05), "were", "were not")

```

- Results `r robustness_contingency_memory` robust to including only participants who were contingency aware, p in subsample `r results_exp_4_h3_contingency_memory$p[results_exp_4_h3_contingency_memory$var == "Struan"]`.
- Results `r robustness_demand_compliance` robust to including only participants who were not demand compliant, p in subsample `r results_exp_4_h3_demand_compliance$p[results_exp_4_h3_demand_compliance$var == "Struan"]`.
- Results `r robustness_hypothesis_aware` robust to including only participants who were not hypothesis aware, p in subsample 
`r results_exp_4_h3_hypothesis_aware$p[results_exp_4_h3_hypothesis_aware$var == "Struan"]`.
- Results `r robustness_influence_aware` robust to including only participants who were not influence aware, p in subsample `r results_exp_4_h3_influence_aware$p[results_exp_4_h3_influence_aware$var == "Struan"]`.

## Experiment 5

### H1: IAT

```{r}

results_exp_5_h1 <- tidied_data_exp_5 %>%
  mutate(DV = IAT_Score,
         IV = Color_Matching) %>%
  t_test_analyses(.)

```

When CS1 eventually shared a color with positive words and CS2 shared a color with negative words, participants showed an automatic relative preference for CS1 over CS2 on the IAT (M = `r format(results_exp_5_h1$summary_stats$mean[results_exp_5_h1$summary_stats$IV == "CS1_Positive_CS2_Negative"], nsmall = 2)`, SD = `r format(results_exp_5_h1$summary_stats$sd[results_exp_5_h1$summary_stats$IV == "CS1_Positive_CS2_Negative"], nsmall = 2)`), whereas when CS1 eventually shared a color with negative words and CS2 shared a color with positive words, they demonstrated a relative preference for CS2 over CS1 (M = `r format(results_exp_5_h1$summary_stats$mean[results_exp_5_h1$summary_stats$IV == "CS2_Positive_CS1_Negative"], nsmall = 2)`, SD = `r format(results_exp_5_h1$summary_stats$sd[results_exp_5_h1$summary_stats$IV == "CS2_Positive_CS1_Negative"], nsmall = 2)`), `r results_exp_5_h1$t_test_output`, BF10 = `r format(results_exp_5_h1$bf10, nsmall = 2)`.

#### Robustness tests

```{r}

full_sample_p_value_exp_5_h1 <- results_exp_5_h1$t_test_p

# re run tests with desired subsets of participants
results_exp_5_h1_contingency_memory <- tidied_data_exp_5 %>%
  #filter(contingency_memory == TRUE) %>%
  mutate(DV = IAT_Score,
         IV = Color_Matching) %>%
  t_test_analyses(.)

results_exp_5_h1_demand_compliance <- tidied_data_exp_5 %>%
  #filter(demand_compliance == FALSE) %>%
  mutate(DV = IAT_Score,
         IV = Color_Matching) %>%
  t_test_analyses(.)

results_exp_5_h1_hypothesis_aware <- tidied_data_exp_5 %>%
  #filter(hypothesis_aware == FALSE) %>%
  mutate(DV = IAT_Score,
         IV = Color_Matching) %>%
  t_test_analyses(.)

results_exp_5_h1_influence_aware <- tidied_data_exp_5 %>%
  #filter(influence_aware == FALSE) %>%
  mutate(DV = IAT_Score,
         IV = Color_Matching) %>%
  t_test_analyses(.)

# robustness strings
robustness_contingency_memory <- 
  ifelse((results_exp_5_h1_contingency_memory$t_test_p < 0.05 & 
            full_sample_p_value_exp_5_h1 < 0.05) |
           (results_exp_5_h1_contingency_memory$t_test_p >= 0.05 & 
              full_sample_p_value_exp_5_h1 >= 0.05), "were", "were not")

robustness_demand_compliance <- 
  ifelse((results_exp_5_h1_demand_compliance$t_test_p < 0.05 & 
            full_sample_p_value_exp_5_h1 < 0.05) |
           (results_exp_5_h1_demand_compliance$t_test_p >= 0.05 & 
              full_sample_p_value_exp_5_h1 >= 0.05), "were", "were not")

robustness_hypothesis_aware <- 
  ifelse((results_exp_5_h1_hypothesis_aware$t_test_p < 0.05 & 
            full_sample_p_value_exp_5_h1 < 0.05) |
           (results_exp_5_h1_hypothesis_aware$t_test_p >= 0.05 & 
              full_sample_p_value_exp_5_h1 >= 0.05), "were", "were not")

robustness_influence_aware <- 
  ifelse((results_exp_5_h1_influence_aware$t_test_p < 0.05 & 
            full_sample_p_value_exp_5_h1 < 0.05) |
           (results_exp_5_h1_influence_aware$t_test_p >= 0.05 & 
              full_sample_p_value_exp_5_h1 >= 0.05), "were", "were not")

```

- Results `r robustness_contingency_memory` robust to including only participants who were contingency aware, p in subsample `r apa_p_value(results_exp_5_h1_contingency_memory$t_test_p)`.
- Results `r robustness_demand_compliance` robust to including only participants who were not demand compliant, p in subsample `r apa_p_value(results_exp_5_h1_demand_compliance$t_test_p)`.
- Results `r robustness_hypothesis_aware` robust to including only participants who were not hypothesis aware, p in subsample `r apa_p_value(results_exp_5_h1_hypothesis_aware$t_test_p)`.
- Results `r robustness_influence_aware` robust to including only participants who were not influence aware, p in subsample `r apa_p_value(results_exp_5_h1_influence_aware$t_test_p)`.

### H2: Self-report ratings

```{r}

results_exp_5_h2 <- tidied_data_exp_5 %>%
  mutate(DV = EC_Effect_CS1_CS2_Difference_Score,
         IV = Color_Matching) %>%
  t_test_analyses(.)

```

When CS1 eventually shared a color with positive words and CS2 shared a color with negative words, participants showed a relative preference on the self-report ratings for CS1 over CS2 (M = `r format(results_exp_5_h2$summary_stats$mean[results_exp_5_h2$summary_stats$IV == "CS1_Positive_CS2_Negative"], nsmall = 2)`, SD = `r format(results_exp_5_h2$summary_stats$sd[results_exp_5_h2$summary_stats$IV == "CS1_Positive_CS2_Negative"], nsmall = 2)`), whereas when CS1 eventually shared a color with negative words and CS2 shared a color with positive words, they demonstrated a relative preference for CS2 over CS1 (M = `r format(results_exp_5_h2$summary_stats$mean[results_exp_5_h2$summary_stats$IV == "CS2_Positive_CS1_Negative"], nsmall = 2)`, SD = `r format(results_exp_5_h2$summary_stats$sd[results_exp_5_h2$summary_stats$IV == "CS2_Positive_CS1_Negative"], nsmall = 2)`), `r results_exp_5_h2$t_test_output`, BF10 = `r format(results_exp_5_h2$bf10, nsmall = 2)`.

#### Robustness tests

```{r}

full_sample_p_value_exp_5_h2 <- results_exp_5_h2$t_test_p

# re run tests with desired subsets of participants
results_exp_5_h2_contingency_memory <- tidied_data_exp_5 %>%
  #filter(contingency_memory == TRUE) %>%
  mutate(DV = EC_Effect_CS1_CS2_Difference_Score,
         IV = Color_Matching) %>%
  t_test_analyses(.)

results_exp_5_h2_demand_compliance <- tidied_data_exp_5 %>%
  #filter(demand_compliance == FALSE) %>%
  mutate(DV = EC_Effect_CS1_CS2_Difference_Score,
         IV = Color_Matching) %>%
  t_test_analyses(.)

results_exp_5_h2_hypothesis_aware <- tidied_data_exp_5 %>%
  #filter(hypothesis_aware == FALSE) %>%
  mutate(DV = EC_Effect_CS1_CS2_Difference_Score,
         IV = Color_Matching) %>%
  t_test_analyses(.)

results_exp_5_h2_influence_aware <- tidied_data_exp_5 %>%
  #filter(influence_aware == FALSE) %>%
  mutate(DV = EC_Effect_CS1_CS2_Difference_Score,
         IV = Color_Matching) %>%
  t_test_analyses(.)

# robustness strings
robustness_contingency_memory <- 
  ifelse((results_exp_5_h2_contingency_memory$t_test_p < 0.05 & 
            full_sample_p_value_exp_5_h2 < 0.05) |
           (results_exp_5_h2_contingency_memory$t_test_p >= 0.05 & 
              full_sample_p_value_exp_5_h2 >= 0.05), "were", "were not")

robustness_demand_compliance <- 
  ifelse((results_exp_5_h2_demand_compliance$t_test_p < 0.05 & 
            full_sample_p_value_exp_5_h2 < 0.05) |
           (results_exp_5_h2_demand_compliance$t_test_p >= 0.05 & 
              full_sample_p_value_exp_5_h2 >= 0.05), "were", "were not")

robustness_hypothesis_aware <- 
  ifelse((results_exp_5_h2_hypothesis_aware$t_test_p < 0.05 & 
            full_sample_p_value_exp_5_h2 < 0.05) |
           (results_exp_5_h2_hypothesis_aware$t_test_p >= 0.05 & 
              full_sample_p_value_exp_5_h2 >= 0.05), "were", "were not")

robustness_influence_aware <- 
  ifelse((results_exp_5_h2_influence_aware$t_test_p < 0.05 & 
            full_sample_p_value_exp_5_h2 < 0.05) |
           (results_exp_5_h2_influence_aware$t_test_p >= 0.05 & 
              full_sample_p_value_exp_5_h2 >= 0.05), "were", "were not")

```

- Results `r robustness_contingency_memory` robust to including only participants who were contingency aware, p in subsample `r apa_p_value(results_exp_5_h2_contingency_memory$t_test_p)`.
- Results `r robustness_demand_compliance` robust to including only participants who were not demand compliant, p in subsample `r apa_p_value(results_exp_5_h2_demand_compliance$t_test_p)`.
- Results `r robustness_hypothesis_aware` robust to including only participants who were not hypothesis aware, p in subsample `r apa_p_value(results_exp_5_h2_hypothesis_aware$t_test_p)`.
- Results `r robustness_influence_aware` robust to including only participants who were not influence aware, p in subsample `r apa_p_value(results_exp_5_h2_influence_aware$t_test_p)`.

### H3: Behavioural intentions

```{r echo=TRUE, results='hide'}

# set reference level to "Morag"
data_for_analysis <- tidied_data_exp_5 
data_for_analysis$intention <- relevel(data_for_analysis$intention, ref = "Morag")

results_exp_5_h3 <- multinominal_analysis(data_for_analysis)

```

Data from the behavioural intentions question were entered into a multinomial logistic regression with CSI as the reference category. Only results from the CS1-CS2 comparison are relevant to the hypothesis and will be reported here. Results demonstrated that participants responses of CS1 relative to CS2 differed between the two conditions, congruent with training, OR = `r format(results_exp_5_h3$OR[results_exp_5_h3$var == "Struan"], nsmall = 2)`, 95% CI = [`r format(results_exp_5_h3$OR_ci_lwr[results_exp_5_h3$var == "Struan"], nsmall = 2)`, `r format(results_exp_5_h3$OR_ci_upr[results_exp_5_h3$var == "Struan"], nsmall = 2)`], p `r results_exp_5_h3$p[results_exp_5_h3$var == "Struan"]`.

#### Robustness tests

```{r echo=TRUE, results='hide'}

full_sample_p_value_exp_5_h3_exp_5_h3 <- results_exp_5_h3$p[results_exp_5_h3$var == "Struan"]

# re run tests with desired subsets of participants
results_exp_5_h3_contingency_memory <- data_for_analysis %>%
  #filter(contingency_memory == TRUE) %>%
  multinominal_analysis(.)

results_exp_5_h3_demand_compliance <- data_for_analysis %>%
  #filter(demand_compliance == FALSE) %>%
  multinominal_analysis(.)

results_exp_5_h3_hypothesis_aware <- data_for_analysis %>%
  #filter(hypothesis_aware == FALSE) %>%
  multinominal_analysis(.)

results_exp_5_h3_influence_aware <- data_for_analysis %>%
  #filter(influence_aware == FALSE) %>%
  multinominal_analysis(.)

# robustness strings
robustness_contingency_memory <-
  ifelse((results_exp_5_h3_contingency_memory$p[results_exp_5_h3$var == "Struan"] < 0.05 & 
            full_sample_p_value_exp_5_h3_exp_5_h3 < 0.05) |
           (results_exp_5_h3_contingency_memory$p[results_exp_5_h3$var == "Struan"] >= 0.05 & 
              full_sample_p_value_exp_5_h3_exp_5_h3 >= 0.05), "were", "were not")

robustness_demand_compliance <-
  ifelse((results_exp_5_h3_demand_compliance$p[results_exp_5_h3$var == "Struan"] < 0.05 & 
            full_sample_p_value_exp_5_h3_exp_5_h3 < 0.05) |
           (results_exp_5_h3_demand_compliance$p[results_exp_5_h3$var == "Struan"] >= 0.05 & 
              full_sample_p_value_exp_5_h3_exp_5_h3 >= 0.05), "were", "were not")

robustness_hypothesis_aware <- 
  ifelse((results_exp_5_h3_hypothesis_aware$p[results_exp_5_h3$var == "Struan"] < 0.05 & 
            full_sample_p_value_exp_5_h3_exp_5_h3 < 0.05) |
           (results_exp_5_h3_hypothesis_aware$p[results_exp_5_h3$var == "Struan"] >= 0.05 & 
              full_sample_p_value_exp_5_h3_exp_5_h3 >= 0.05), "were", "were not")

robustness_influence_aware <- 
  ifelse((results_exp_5_h3_influence_aware$p[results_exp_5_h3$var == "Struan"] < 0.05 & 
            full_sample_p_value_exp_5_h3_exp_5_h3 < 0.05) |
           (results_exp_5_h3_influence_aware$p[results_exp_5_h3$var == "Struan"] >= 0.05 & 
              full_sample_p_value_exp_5_h3_exp_5_h3 >= 0.05), "were", "were not")

```

- Results `r robustness_contingency_memory` robust to including only participants who were contingency aware, p in subsample `r results_exp_5_h3_contingency_memory$p[results_exp_5_h3_contingency_memory$var == "Struan"]`.
- Results `r robustness_demand_compliance` robust to including only participants who were not demand compliant, p in subsample `r results_exp_5_h3_demand_compliance$p[results_exp_5_h3_demand_compliance$var == "Struan"]`.
- Results `r robustness_hypothesis_aware` robust to including only participants who were not hypothesis aware, p in subsample 
`r results_exp_5_h3_hypothesis_aware$p[results_exp_5_h3_hypothesis_aware$var == "Struan"]`.
- Results `r robustness_influence_aware` robust to including only participants who were not influence aware, p in subsample `r results_exp_5_h3_influence_aware$p[results_exp_5_h3_influence_aware$var == "Struan"]`.

# Meta analyses

## H1: IAT

```{r}

results_for_meta_analysis_h1 <- 
  data.frame(Experiment = c(1, 2, 3, 4, 5),
             cohens_d = c(results_exp_1_h1$cohens_d$estimate[[1]], 
                          results_exp_2_h1$cohens_d$estimate[[1]], 
                          results_exp_3_h1$cohens_d$estimate[[1]], 
                          results_exp_4_h1$cohens_d$estimate[[1]],
                          results_exp_5_h1$cohens_d$estimate[[1]]),
             ci_lwr = c(results_exp_1_h1$cohens_d$conf.int[["inf"]],
                        results_exp_2_h1$cohens_d$conf.int[["inf"]],
                        results_exp_3_h1$cohens_d$conf.int[["inf"]],
                        results_exp_4_h1$cohens_d$conf.int[["inf"]],
                        results_exp_5_h1$cohens_d$conf.int[["inf"]]),
             ci_upr = c(results_exp_1_h1$cohens_d$conf.int[["sup"]],
                        results_exp_2_h1$cohens_d$conf.int[["sup"]],
                        results_exp_3_h1$cohens_d$conf.int[["sup"]],
                        results_exp_4_h1$cohens_d$conf.int[["sup"]],
                        results_exp_5_h1$cohens_d$conf.int[["sup"]])) %>%
  mutate(yi = cohens_d, 
         sei = (ci_upr - ci_lwr)/(1.96*2))

meta_results_h1 <- meta_analysis_workflow(data              = results_for_meta_analysis_h1,
                                          effect_size_label = "Cohen's d",
                                          exp_estimates     = FALSE,
                                          reference_line    = 0)

```

- Meta analysis: `r meta_results_h1$meta_analysis_results_text`
- Heterogeneity tests: `r meta_results_h1$heterogeneity_test_results_text`

### Robustness tests

```{r echo=TRUE, results='hide'}

# contingency_memory
results_for_meta_analysis_h1_contingency_memory <- 
  data.frame(Experiment = c(1,2,3,4,5),
             cohens_d = c(results_exp_1_h1_contingency_memory$cohens_d$estimate[[1]], 
                          results_exp_2_h1_contingency_memory$cohens_d$estimate[[1]], 
                          results_exp_3_h1_contingency_memory$cohens_d$estimate[[1]], 
                          results_exp_4_h1_contingency_memory$cohens_d$estimate[[1]],
                          results_exp_5_h1_contingency_memory$cohens_d$estimate[[1]]),
             ci_lwr = c(results_exp_1_h1_contingency_memory$cohens_d$conf.int[["inf"]],
                        results_exp_2_h1_contingency_memory$cohens_d$conf.int[["inf"]],
                        results_exp_3_h1_contingency_memory$cohens_d$conf.int[["inf"]],
                        results_exp_4_h1_contingency_memory$cohens_d$conf.int[["inf"]],
                        results_exp_5_h1_contingency_memory$cohens_d$conf.int[["inf"]]),
             ci_upr = c(results_exp_1_h1_contingency_memory$cohens_d$conf.int[["sup"]],
                        results_exp_2_h1_contingency_memory$cohens_d$conf.int[["sup"]],
                        results_exp_3_h1_contingency_memory$cohens_d$conf.int[["sup"]],
                        results_exp_4_h1_contingency_memory$cohens_d$conf.int[["sup"]],
                        results_exp_5_h1_contingency_memory$cohens_d$conf.int[["sup"]])) %>%
  mutate(yi = cohens_d, 
         sei = (ci_upr - ci_lwr)/(1.96*2))

meta_results_h1_contingency_memory <- 
  meta_analysis_workflow(data              = results_for_meta_analysis_h1_contingency_memory,
                         effect_size_label = "Cohen's d",
                         exp_estimates     = FALSE,
                         reference_line    = 0,
                         plot = FALSE)

# demand_compliance
results_for_meta_analysis_h1_demand_compliance <- 
  data.frame(Experiment = c(1,2,3,4,5),
             cohens_d = c(results_exp_1_h1_demand_compliance$cohens_d$estimate[[1]], 
                          results_exp_2_h1_demand_compliance$cohens_d$estimate[[1]], 
                          results_exp_3_h1_demand_compliance$cohens_d$estimate[[1]], 
                          results_exp_4_h1_demand_compliance$cohens_d$estimate[[1]],
                          results_exp_5_h1_demand_compliance$cohens_d$estimate[[1]]),
             ci_lwr = c(results_exp_1_h1_demand_compliance$cohens_d$conf.int[["inf"]],
                        results_exp_2_h1_demand_compliance$cohens_d$conf.int[["inf"]],
                        results_exp_3_h1_demand_compliance$cohens_d$conf.int[["inf"]],
                        results_exp_4_h1_demand_compliance$cohens_d$conf.int[["inf"]],
                        results_exp_5_h1_demand_compliance$cohens_d$conf.int[["inf"]]),
             ci_upr = c(results_exp_1_h1_demand_compliance$cohens_d$conf.int[["sup"]],
                        results_exp_2_h1_demand_compliance$cohens_d$conf.int[["sup"]],
                        results_exp_3_h1_demand_compliance$cohens_d$conf.int[["sup"]],
                        results_exp_4_h1_demand_compliance$cohens_d$conf.int[["sup"]],
                        results_exp_5_h1_demand_compliance$cohens_d$conf.int[["sup"]])) %>%
  mutate(yi = cohens_d, 
         sei = (ci_upr - ci_lwr)/(1.96*2))

meta_results_h1_demand_compliance <- 
  meta_analysis_workflow(data              = results_for_meta_analysis_h1_demand_compliance,
                         effect_size_label = "Cohen's d",
                         exp_estimates     = FALSE,
                         reference_line    = 0,
                         plot = FALSE)

# hypothesis_aware
results_for_meta_analysis_h1_hypothesis_aware <- 
  data.frame(Experiment = c(1,2,3,4,5),
             cohens_d = c(results_exp_1_h1_hypothesis_aware$cohens_d$estimate[[1]], 
                          results_exp_2_h1_hypothesis_aware$cohens_d$estimate[[1]], 
                          results_exp_3_h1_hypothesis_aware$cohens_d$estimate[[1]], 
                          results_exp_4_h1_hypothesis_aware$cohens_d$estimate[[1]],
                          results_exp_5_h1_hypothesis_aware$cohens_d$estimate[[1]]),
             ci_lwr = c(results_exp_1_h1_hypothesis_aware$cohens_d$conf.int[["inf"]],
                        results_exp_2_h1_hypothesis_aware$cohens_d$conf.int[["inf"]],
                        results_exp_3_h1_hypothesis_aware$cohens_d$conf.int[["inf"]],
                        results_exp_4_h1_hypothesis_aware$cohens_d$conf.int[["inf"]],
                        results_exp_5_h1_hypothesis_aware$cohens_d$conf.int[["inf"]]),
             ci_upr = c(results_exp_1_h1_hypothesis_aware$cohens_d$conf.int[["sup"]],
                        results_exp_2_h1_hypothesis_aware$cohens_d$conf.int[["sup"]],
                        results_exp_3_h1_hypothesis_aware$cohens_d$conf.int[["sup"]],
                        results_exp_4_h1_hypothesis_aware$cohens_d$conf.int[["sup"]],
                        results_exp_5_h1_hypothesis_aware$cohens_d$conf.int[["sup"]])) %>%
  mutate(yi = cohens_d, 
         sei = (ci_upr - ci_lwr)/(1.96*2))

meta_results_h1_hypothesis_aware <- 
  meta_analysis_workflow(data              = results_for_meta_analysis_h1_hypothesis_aware,
                         effect_size_label = "Cohen's d",
                         exp_estimates     = FALSE,
                         reference_line    = 0,
                         plot = FALSE)

# influence_aware
results_for_meta_analysis_h1_influence_aware <- 
  data.frame(Experiment = c(1,2,3,4,5),
             cohens_d = c(results_exp_1_h1_influence_aware$cohens_d$estimate[[1]], 
                          results_exp_2_h1_influence_aware$cohens_d$estimate[[1]], 
                          results_exp_3_h1_influence_aware$cohens_d$estimate[[1]], 
                          results_exp_4_h1_influence_aware$cohens_d$estimate[[1]],
                          results_exp_5_h1_influence_aware$cohens_d$estimate[[1]]),
             ci_lwr = c(results_exp_1_h1_influence_aware$cohens_d$conf.int[["inf"]],
                        results_exp_2_h1_influence_aware$cohens_d$conf.int[["inf"]],
                        results_exp_3_h1_influence_aware$cohens_d$conf.int[["inf"]],
                        results_exp_4_h1_influence_aware$cohens_d$conf.int[["inf"]],
                        results_exp_5_h1_influence_aware$cohens_d$conf.int[["inf"]]),
             ci_upr = c(results_exp_1_h1_influence_aware$cohens_d$conf.int[["sup"]],
                        results_exp_2_h1_influence_aware$cohens_d$conf.int[["sup"]],
                        results_exp_3_h1_influence_aware$cohens_d$conf.int[["sup"]],
                        results_exp_4_h1_influence_aware$cohens_d$conf.int[["sup"]],
                        results_exp_5_h1_influence_aware$cohens_d$conf.int[["sup"]])) %>%
  mutate(yi = cohens_d, 
         sei = (ci_upr - ci_lwr)/(1.96*2))

meta_results_h1_influence_aware <- 
  meta_analysis_workflow(data              = results_for_meta_analysis_h1_influence_aware,
                         effect_size_label = "Cohen's d",
                         exp_estimates     = FALSE,
                         reference_line    = 0,
                         plot = FALSE)

# robustness strings
robustness_contingency_memory <-
  ifelse(robust_test(meta_results_h1_contingency_memory$meta_analysis_results, 
                     meta_results_h1$meta_analysis_results),
         "were", "were not")

robustness_demand_compliance  <-
  ifelse(robust_test(meta_results_h1_demand_compliance$meta_analysis_results, 
                     meta_results_h1$meta_analysis_results),
         "were", "were not")

robustness_hypothesis_aware   <-
  ifelse(robust_test(meta_results_h1_hypothesis_aware$meta_analysis_results, 
                     meta_results_h1$meta_analysis_results),
         "were", "were not")

robustness_influence_aware    <-
  ifelse(robust_test(meta_results_h1_influence_aware$meta_analysis_results, 
                     meta_results_h1$meta_analysis_results),
         "were", "were not")

```

- Across studies, results `r robustness_contingency_memory` robust to including only participants who were contingency aware, p in subsample `r meta_results_h1_contingency_memory$meta_analysis_results$estimate[meta_results_h1_contingency_memory$meta_analysis_results$metric == "p"]`.
- Across studies, results `r robustness_demand_compliance` robust to including only participants who were not demand compliant, p in subsample `r meta_results_h1_demand_compliance$meta_analysis_results$estimate[meta_results_h1_demand_compliance$meta_analysis_results$metric == "p"]`.
- Across studies, results `r robustness_hypothesis_aware` robust to including only participants who were not hypothesis aware, p in subsample `r meta_results_h1_hypothesis_aware$meta_analysis_results$estimate[meta_results_h1_hypothesis_aware$meta_analysis_results$metric == "p"]`.
- Across studies, results `r robustness_influence_aware` robust to including only participants who were not influence aware, p in subsample `r meta_results_h1_influence_aware$meta_analysis_results$estimate[meta_results_h1_influence_aware$meta_analysis_results$metric == "p"]`.

## H2: Self-report ratings

```{r}

results_for_meta_analysis_h2 <- 
  data.frame(Experiment = c(1, 2, 3, 4, 5),
             cohens_d = c(results_exp_1_h2$cohens_d$estimate[[1]], 
                          results_exp_2_h2$cohens_d$estimate[[1]], 
                          results_exp_3_h2$cohens_d$estimate[[1]], 
                          results_exp_4_h2$cohens_d$estimate[[1]],
                          results_exp_5_h2$cohens_d$estimate[[1]]),
             ci_lwr = c(results_exp_1_h2$cohens_d$conf.int[["inf"]],
                        results_exp_2_h2$cohens_d$conf.int[["inf"]],
                        results_exp_3_h2$cohens_d$conf.int[["inf"]],
                        results_exp_4_h2$cohens_d$conf.int[["inf"]],
                        results_exp_5_h2$cohens_d$conf.int[["inf"]]),
             ci_upr = c(results_exp_1_h2$cohens_d$conf.int[["sup"]],
                        results_exp_2_h2$cohens_d$conf.int[["sup"]],
                        results_exp_3_h2$cohens_d$conf.int[["sup"]],
                        results_exp_4_h2$cohens_d$conf.int[["sup"]],
                        results_exp_5_h2$cohens_d$conf.int[["sup"]])) %>%
  mutate(yi = cohens_d, 
         sei = (ci_upr - ci_lwr)/(1.96*2))

meta_results_h2 <- meta_analysis_workflow(data              = results_for_meta_analysis_h2,
                                          effect_size_label = "Cohen's d",
                                          exp_estimates     = FALSE,
                                          reference_line    = 0)

```

- Meta analysis: `r meta_results_h2$meta_analysis_results_text`
- Heterogeneity tests: `r meta_results_h2$heterogeneity_test_results_text`

### Robustness tests

```{r echo=TRUE, results='hide'}

# contingency_memory
results_for_meta_analysis_h2_contingency_memory <- 
  data.frame(Experiment = c(1,2,3,4,5),
             cohens_d = c(results_exp_1_h2_contingency_memory$cohens_d$estimate[[1]], 
                          results_exp_2_h2_contingency_memory$cohens_d$estimate[[1]], 
                          results_exp_3_h2_contingency_memory$cohens_d$estimate[[1]], 
                          results_exp_4_h2_contingency_memory$cohens_d$estimate[[1]],
                          results_exp_5_h2_contingency_memory$cohens_d$estimate[[1]]),
             ci_lwr = c(results_exp_1_h2_contingency_memory$cohens_d$conf.int[["inf"]],
                        results_exp_2_h2_contingency_memory$cohens_d$conf.int[["inf"]],
                        results_exp_3_h2_contingency_memory$cohens_d$conf.int[["inf"]],
                        results_exp_4_h2_contingency_memory$cohens_d$conf.int[["inf"]],
                        results_exp_5_h2_contingency_memory$cohens_d$conf.int[["inf"]]),
             ci_upr = c(results_exp_1_h2_contingency_memory$cohens_d$conf.int[["sup"]],
                        results_exp_2_h2_contingency_memory$cohens_d$conf.int[["sup"]],
                        results_exp_3_h2_contingency_memory$cohens_d$conf.int[["sup"]],
                        results_exp_4_h2_contingency_memory$cohens_d$conf.int[["sup"]],
                        results_exp_5_h2_contingency_memory$cohens_d$conf.int[["sup"]])) %>%
  mutate(yi = cohens_d, 
         sei = (ci_upr - ci_lwr)/(1.96*2))

meta_results_h2_contingency_memory <- 
  meta_analysis_workflow(data              = results_for_meta_analysis_h2_contingency_memory,
                         effect_size_label = "Cohen's d",
                         exp_estimates     = FALSE,
                         reference_line    = 0,
                         plot = FALSE)

# demand_compliance
results_for_meta_analysis_h2_demand_compliance <- 
  data.frame(Experiment = c(1,2,3,4,5),
             cohens_d = c(results_exp_1_h2_demand_compliance$cohens_d$estimate[[1]], 
                          results_exp_2_h2_demand_compliance$cohens_d$estimate[[1]], 
                          results_exp_3_h2_demand_compliance$cohens_d$estimate[[1]], 
                          results_exp_4_h2_demand_compliance$cohens_d$estimate[[1]],
                          results_exp_5_h2_demand_compliance$cohens_d$estimate[[1]]),
             ci_lwr = c(results_exp_1_h2_demand_compliance$cohens_d$conf.int[["inf"]],
                        results_exp_2_h2_demand_compliance$cohens_d$conf.int[["inf"]],
                        results_exp_3_h2_demand_compliance$cohens_d$conf.int[["inf"]],
                        results_exp_4_h2_demand_compliance$cohens_d$conf.int[["inf"]],
                        results_exp_5_h2_demand_compliance$cohens_d$conf.int[["inf"]]),
             ci_upr = c(results_exp_1_h2_demand_compliance$cohens_d$conf.int[["sup"]],
                        results_exp_2_h2_demand_compliance$cohens_d$conf.int[["sup"]],
                        results_exp_3_h2_demand_compliance$cohens_d$conf.int[["sup"]],
                        results_exp_4_h2_demand_compliance$cohens_d$conf.int[["sup"]],
                        results_exp_5_h2_demand_compliance$cohens_d$conf.int[["sup"]])) %>%
  mutate(yi = cohens_d, 
         sei = (ci_upr - ci_lwr)/(1.96*2))

meta_results_h2_demand_compliance <- 
  meta_analysis_workflow(data              = results_for_meta_analysis_h2_demand_compliance,
                         effect_size_label = "Cohen's d",
                         exp_estimates     = FALSE,
                         reference_line    = 0,
                         plot = FALSE)

# hypothesis_aware
results_for_meta_analysis_h2_hypothesis_aware <- 
  data.frame(Experiment = c(1,2,3,4,5),
             cohens_d = c(results_exp_1_h2_hypothesis_aware$cohens_d$estimate[[1]], 
                          results_exp_2_h2_hypothesis_aware$cohens_d$estimate[[1]], 
                          results_exp_3_h2_hypothesis_aware$cohens_d$estimate[[1]], 
                          results_exp_4_h2_hypothesis_aware$cohens_d$estimate[[1]],
                          results_exp_5_h2_hypothesis_aware$cohens_d$estimate[[1]]),
             ci_lwr = c(results_exp_1_h2_hypothesis_aware$cohens_d$conf.int[["inf"]],
                        results_exp_2_h2_hypothesis_aware$cohens_d$conf.int[["inf"]],
                        results_exp_3_h2_hypothesis_aware$cohens_d$conf.int[["inf"]],
                        results_exp_4_h2_hypothesis_aware$cohens_d$conf.int[["inf"]],
                        results_exp_5_h2_hypothesis_aware$cohens_d$conf.int[["inf"]]),
             ci_upr = c(results_exp_1_h2_hypothesis_aware$cohens_d$conf.int[["sup"]],
                        results_exp_2_h2_hypothesis_aware$cohens_d$conf.int[["sup"]],
                        results_exp_3_h2_hypothesis_aware$cohens_d$conf.int[["sup"]],
                        results_exp_4_h2_hypothesis_aware$cohens_d$conf.int[["sup"]],
                        results_exp_5_h2_hypothesis_aware$cohens_d$conf.int[["sup"]])) %>%
  mutate(yi = cohens_d, 
         sei = (ci_upr - ci_lwr)/(1.96*2))

meta_results_h2_hypothesis_aware <- 
  meta_analysis_workflow(data              = results_for_meta_analysis_h2_hypothesis_aware,
                         effect_size_label = "Cohen's d",
                         exp_estimates     = FALSE,
                         reference_line    = 0,
                         plot = FALSE)

# influence_aware
results_for_meta_analysis_h2_influence_aware <- 
  data.frame(Experiment = c(1,2,3,4,5),
             cohens_d = c(results_exp_1_h2_influence_aware$cohens_d$estimate[[1]], 
                          results_exp_2_h2_influence_aware$cohens_d$estimate[[1]], 
                          results_exp_3_h2_influence_aware$cohens_d$estimate[[1]], 
                          results_exp_4_h2_influence_aware$cohens_d$estimate[[1]],
                          results_exp_5_h2_influence_aware$cohens_d$estimate[[1]]),
             ci_lwr = c(results_exp_1_h2_influence_aware$cohens_d$conf.int[["inf"]],
                        results_exp_2_h2_influence_aware$cohens_d$conf.int[["inf"]],
                        results_exp_3_h2_influence_aware$cohens_d$conf.int[["inf"]],
                        results_exp_4_h2_influence_aware$cohens_d$conf.int[["inf"]],
                        results_exp_5_h2_influence_aware$cohens_d$conf.int[["inf"]]),
             ci_upr = c(results_exp_1_h2_influence_aware$cohens_d$conf.int[["sup"]],
                        results_exp_2_h2_influence_aware$cohens_d$conf.int[["sup"]],
                        results_exp_3_h2_influence_aware$cohens_d$conf.int[["sup"]],
                        results_exp_4_h2_influence_aware$cohens_d$conf.int[["sup"]],
                        results_exp_5_h2_influence_aware$cohens_d$conf.int[["sup"]])) %>%
  mutate(yi = cohens_d, 
         sei = (ci_upr - ci_lwr)/(1.96*2))

meta_results_h2_influence_aware <- 
  meta_analysis_workflow(data              = results_for_meta_analysis_h2_influence_aware,
                         effect_size_label = "Cohen's d",
                         exp_estimates     = FALSE,
                         reference_line    = 0,
                         plot = FALSE)

# robustness strings
robustness_contingency_memory <-
  ifelse(robust_test(meta_results_h2_contingency_memory$meta_analysis_results, 
                     meta_results_h1$meta_analysis_results),
         "were", "were not")

robustness_demand_compliance  <-
  ifelse(robust_test(meta_results_h2_demand_compliance$meta_analysis_results, 
                     meta_results_h1$meta_analysis_results),
         "were", "were not")

robustness_hypothesis_aware   <-
  ifelse(robust_test(meta_results_h2_hypothesis_aware$meta_analysis_results, 
                     meta_results_h1$meta_analysis_results),
         "were", "were not")

robustness_influence_aware    <-
  ifelse(robust_test(meta_results_h2_influence_aware$meta_analysis_results, 
                     meta_results_h1$meta_analysis_results),
         "were", "were not")

```

- Across studies, results `r robustness_contingency_memory` robust to including only participants who were contingency aware, p in subsample `r meta_results_h2_contingency_memory$meta_analysis_results$estimate[meta_results_h2_contingency_memory$meta_analysis_results$metric == "p"]`.
- Across studies, results `r robustness_demand_compliance` robust to including only participants who were not demand compliant, p in subsample `r meta_results_h2_demand_compliance$meta_analysis_results$estimate[meta_results_h2_demand_compliance$meta_analysis_results$metric == "p"]`.
- Across studies, results `r robustness_hypothesis_aware` robust to including only participants who were not hypothesis aware, p in subsample `r meta_results_h2_hypothesis_aware$meta_analysis_results$estimate[meta_results_h2_hypothesis_aware$meta_analysis_results$metric == "p"]`.
- Across studies, results `r robustness_influence_aware` robust to including only participants who were not influence aware, p in subsample `r meta_results_h2_influence_aware$meta_analysis_results$estimate[meta_results_h2_influence_aware$meta_analysis_results$metric == "p"]`.

## H3: Behavioural intentions

```{r echo=TRUE, results='hide'}

results_for_meta_analysis_h3 <- 
  data.frame(Experiment = c(1, 2, 3, 4, 5),
             logOR = c(results_exp_1_h3$logOR[results_exp_1_h3$var == "Struan"], 
                       results_exp_2_h3$logOR[results_exp_2_h3$var == "Struan"],
                       results_exp_3_h3$logOR[results_exp_3_h3$var == "Struan"],
                       results_exp_4_h3$logOR[results_exp_4_h3$var == "Struan"],
                       results_exp_5_h3$logOR[results_exp_5_h3$var == "Struan"]),
             logOR_se = c(results_exp_1_h3$logOR_se[results_exp_1_h3$var == "Struan"],
                          results_exp_2_h3$logOR_se[results_exp_2_h3$var == "Struan"],
                          results_exp_3_h3$logOR_se[results_exp_3_h3$var == "Struan"],
                          results_exp_4_h3$logOR_se[results_exp_4_h3$var == "Struan"],
                          results_exp_5_h3$logOR_se[results_exp_5_h3$var == "Struan"])) %>%
  mutate(yi  = logOR,
         sei = logOR_se)

meta_results_h3 <- meta_analysis_workflow(data = results_for_meta_analysis_h3,
                                          effect_size_label = "Odds Ratio",
                                          exp_estimates     = TRUE,
                                          reference_line    = 0)

```

- Meta analysis: `r meta_results_h3$meta_analysis_results_text`
- Heterogeneity tests: `r meta_results_h3$heterogeneity_test_results_text`

### Robustness tests

```{r echo=TRUE, results='hide'}

results_for_meta_analysis_h3_contingency_memory <- 
  data.frame(Experiment = c(1, 2, 3, 4, 5),
             logOR = c(results_exp_1_h3_contingency_memory$logOR[results_exp_1_h3_contingency_memory$var == "Struan"], 
                       results_exp_2_h3_contingency_memory$logOR[results_exp_2_h3_contingency_memory$var == "Struan"],
                       results_exp_3_h3_contingency_memory$logOR[results_exp_3_h3_contingency_memory$var == "Struan"],
                       results_exp_4_h3_contingency_memory$logOR[results_exp_4_h3_contingency_memory$var == "Struan"],
                       results_exp_5_h3_contingency_memory$logOR[results_exp_5_h3_contingency_memory$var == "Struan"]),
             logOR_se = c(results_exp_1_h3_contingency_memory$logOR_se[results_exp_1_h3_contingency_memory$var == "Struan"],
                          results_exp_2_h3_contingency_memory$logOR_se[results_exp_2_h3_contingency_memory$var == "Struan"],
                          results_exp_3_h3_contingency_memory$logOR_se[results_exp_3_h3_contingency_memory$var == "Struan"],
                          results_exp_4_h3_contingency_memory$logOR_se[results_exp_4_h3_contingency_memory$var == "Struan"],
                          results_exp_5_h3_contingency_memory$logOR_se[results_exp_5_h3_contingency_memory$var == "Struan"])) %>%
  mutate(yi  = logOR,
         sei = logOR_se)

meta_results_h3_contingency_memory <- 
  meta_analysis_workflow(data = results_for_meta_analysis_h3_contingency_memory,
                         effect_size_label = "Odds Ratio",
                         exp_estimates     = TRUE,
                         reference_line    = 0,
                         plot = FALSE)


results_for_meta_analysis_h3_demand_compliance <- 
  data.frame(Experiment = c(1, 2, 3, 4, 5),
             logOR = c(results_exp_1_h3_demand_compliance$logOR[results_exp_1_h3_demand_compliance$var == "Struan"], 
                       results_exp_2_h3_demand_compliance$logOR[results_exp_2_h3_demand_compliance$var == "Struan"],
                       results_exp_3_h3_demand_compliance$logOR[results_exp_3_h3_demand_compliance$var == "Struan"],
                       results_exp_4_h3_demand_compliance$logOR[results_exp_4_h3_demand_compliance$var == "Struan"],
                       results_exp_5_h3_demand_compliance$logOR[results_exp_5_h3_demand_compliance$var == "Struan"]),
             logOR_se = c(results_exp_1_h3_demand_compliance$logOR_se[results_exp_1_h3_demand_compliance$var == "Struan"],
                          results_exp_2_h3_demand_compliance$logOR_se[results_exp_2_h3_demand_compliance$var == "Struan"],
                          results_exp_3_h3_demand_compliance$logOR_se[results_exp_3_h3_demand_compliance$var == "Struan"],
                          results_exp_4_h3_demand_compliance$logOR_se[results_exp_4_h3_demand_compliance$var == "Struan"],
                          results_exp_5_h3_demand_compliance$logOR_se[results_exp_5_h3_demand_compliance$var == "Struan"])) %>%
  mutate(yi  = logOR,
         sei = logOR_se)

meta_results_h3_demand_compliance <- 
  meta_analysis_workflow(data = results_for_meta_analysis_h3_demand_compliance,
                         effect_size_label = "Odds Ratio",
                         exp_estimates     = TRUE,
                         reference_line    = 0,
                         plot = FALSE)


results_for_meta_analysis_h3_hypothesis_aware <- 
  data.frame(Experiment = c(1, 2, 3, 4, 5),
             logOR = c(results_exp_1_h3_hypothesis_aware$logOR[results_exp_1_h3_hypothesis_aware$var == "Struan"], 
                       results_exp_2_h3_hypothesis_aware$logOR[results_exp_2_h3_hypothesis_aware$var == "Struan"],
                       results_exp_3_h3_hypothesis_aware$logOR[results_exp_3_h3_hypothesis_aware$var == "Struan"],
                       results_exp_4_h3_hypothesis_aware$logOR[results_exp_4_h3_hypothesis_aware$var == "Struan"],
                       results_exp_5_h3_hypothesis_aware$logOR[results_exp_5_h3_hypothesis_aware$var == "Struan"]),
             logOR_se = c(results_exp_1_h3_hypothesis_aware$logOR_se[results_exp_1_h3_hypothesis_aware$var == "Struan"],
                          results_exp_2_h3_hypothesis_aware$logOR_se[results_exp_2_h3_hypothesis_aware$var == "Struan"],
                          results_exp_3_h3_hypothesis_aware$logOR_se[results_exp_3_h3_hypothesis_aware$var == "Struan"],
                          results_exp_4_h3_hypothesis_aware$logOR_se[results_exp_4_h3_hypothesis_aware$var == "Struan"],
                          results_exp_5_h3_hypothesis_aware$logOR_se[results_exp_5_h3_hypothesis_aware$var == "Struan"])) %>%
  mutate(yi  = logOR,
         sei = logOR_se)

meta_results_h3_hypothesis_aware <- 
  meta_analysis_workflow(data = results_for_meta_analysis_h3_hypothesis_aware,
                         effect_size_label = "Odds Ratio",
                         exp_estimates     = TRUE,
                         reference_line    = 0,
                         plot = FALSE)


results_for_meta_analysis_h3_influence_aware <- 
  data.frame(Experiment = c(1, 2, 3, 4, 5),
             logOR = c(results_exp_1_h3_influence_aware$logOR[results_exp_1_h3_influence_aware$var == "Struan"], 
                       results_exp_2_h3_influence_aware$logOR[results_exp_2_h3_influence_aware$var == "Struan"],
                       results_exp_3_h3_influence_aware$logOR[results_exp_3_h3_influence_aware$var == "Struan"],
                       results_exp_4_h3_influence_aware$logOR[results_exp_4_h3_influence_aware$var == "Struan"],
                       results_exp_5_h3_influence_aware$logOR[results_exp_5_h3_influence_aware$var == "Struan"]),
             logOR_se = c(results_exp_1_h3_influence_aware$logOR_se[results_exp_1_h3_influence_aware$var == "Struan"],
                          results_exp_2_h3_influence_aware$logOR_se[results_exp_2_h3_influence_aware$var == "Struan"],
                          results_exp_3_h3_influence_aware$logOR_se[results_exp_3_h3_influence_aware$var == "Struan"],
                          results_exp_4_h3_influence_aware$logOR_se[results_exp_4_h3_influence_aware$var == "Struan"],
                          results_exp_5_h3_influence_aware$logOR_se[results_exp_5_h3_influence_aware$var == "Struan"])) %>%
  mutate(yi  = logOR,
         sei = logOR_se)

meta_results_h3_influence_aware <- 
  meta_analysis_workflow(data = results_for_meta_analysis_h3_influence_aware,
                         effect_size_label = "Odds Ratio",
                         exp_estimates     = TRUE,
                         reference_line    = 0,
                         plot = FALSE)

# robustness strings
robustness_contingency_memory <-
  ifelse(robust_test(meta_results_h3_contingency_memory$meta_analysis_results, 
                     meta_results_h1$meta_analysis_results),
         "were", "were not")

robustness_demand_compliance  <-
  ifelse(robust_test(meta_results_h3_demand_compliance$meta_analysis_results, 
                     meta_results_h1$meta_analysis_results),
         "were", "were not")

robustness_hypothesis_aware   <-
  ifelse(robust_test(meta_results_h3_hypothesis_aware$meta_analysis_results, 
                     meta_results_h1$meta_analysis_results),
         "were", "were not")

robustness_influence_aware    <-
  ifelse(robust_test(meta_results_h3_influence_aware$meta_analysis_results, 
                     meta_results_h1$meta_analysis_results),
         "were", "were not")

```

- Across studies, results `r robustness_contingency_memory` robust to including only participants who were contingency aware, p in subsample `r meta_results_h3_contingency_memory$meta_analysis_results$estimate[meta_results_h3_contingency_memory$meta_analysis_results$metric == "p"]`.
- Across studies, results `r robustness_demand_compliance` robust to including only participants who were not demand compliant, p in subsample `r meta_results_h3_demand_compliance$meta_analysis_results$estimate[meta_results_h3_demand_compliance$meta_analysis_results$metric == "p"]`.
- Across studies, results `r robustness_hypothesis_aware` robust to including only participants who were not hypothesis aware, p in subsample `r meta_results_h3_hypothesis_aware$meta_analysis_results$estimate[meta_results_h3_hypothesis_aware$meta_analysis_results$metric == "p"]`.
- Across studies, results `r robustness_influence_aware` robust to including only participants who were not influence aware, p in subsample `r meta_results_h3_influence_aware$meta_analysis_results$estimate[meta_results_h3_influence_aware$meta_analysis_results$metric == "p"]`.

# Plots

## Distribution of IAT and ratings in Experiment 2

Experiment 3 was informed by the unexpected results of experiment 2, which prompted us to examine the distribution of scores on the IAT and self reports which suggested bi- and tri-modality. This is depicted below.

```{r}

tidied_data_exp_2 %>%
  select(Participant, Color_Matching, IAT_Score, EC_Effect_CS1_CS2_Difference_Score) %>%
  rename(`IAT D score` = IAT_Score,
         `Ratings difference score` = EC_Effect_CS1_CS2_Difference_Score) %>%
  gather(dv_modality, dv_score, c(`IAT D score`, `Ratings difference score`)) %>%
  ggplot(aes(dv_score)) +
  geom_density(adjust = 0.5) +
  facet_wrap(~dv_modality+Color_Matching, scales = "free") +
  theme_classic() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        strip.background = element_blank(),
        panel.border = element_blank()) +
  xlab("") +
  ylab("Probability density")

```

