---
title: "Data processing"
author: "Ian Hussey"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    code_folding: hide
    highlight: haddock
    number_sections: no
    theme: flatly
    toc: yes
    toc_float: yes
---

For each study, the raw inquisit data files (xlsx files in the data/raw folder) were processed into a SPSS .sav files by Sean/Simone. This was done manually/in SPSS and no code/syntax to reproduce this processing is available, although it was carefully rechecked in each case. 

The processing.Rmd file in the analysis folder converts all these .sav files first to .csv format (which are saved to the data/processed folders in each experiment) as "data_spss_converted_to_csv.csv". This processing.Rmd script then tidied each data file's names and applied the exclusion criteria. Each experiment's to-be-analyzed data was then saved to the data/processed folder as data_for_analysis.csv.  

In the case of experiment 7, a reviewer's comment required us to reprocess the evaluative priming data. An R script was written for this, which is present in data/processed (i.e., processing_evalautive_priming.Rmd). In order to integrate the manually processed data .sav file with the newer and more reproducible EP data processed via R script, the overall project's data processing script (found at analysis/processing.Rmd and which produces data/processed/processed_ep_data.csv) first reads in the .sav file, discards the columns referring to EP scores, then reads in the newly produced EP scores from processed_ep_data.csv and combines these two files. The resultant data_processed.csv file for experiment 7 therefore represents a combination of the manually and code-based processing of the data for that study. 

```{r, include=FALSE}
knitr::opts_chunk$set(message = FALSE,
                      warning = FALSE)
```

```{r}

# disable scientific notation
options(scipen = 999) 

# dependencies
library(tidyverse)
library(foreign)

```

# Data processing

```{r}

# convert SPSS to csv
input_data_exp_1 <- 
  read.spss("../experiment 1/data/processed/Shared_Features_Study_1_FINAL.sav", to.data.frame = TRUE)

input_data_exp_2 <- 
  read.spss("../experiment 2/data/processed/Shared_Features_Study_2_FINAL.sav", to.data.frame = TRUE)

input_data_exp_3 <- 
  read.spss("../experiment 3/data/processed/Shared_Features_Study_3_FINAL.sav", to.data.frame = TRUE)

input_data_exp_4 <- 
  read.spss("../experiment 4/data/processed/Shared_Features_Study_4_FINAL.sav", to.data.frame = TRUE)

input_data_exp_5 <- 
  read.spss("../experiment 5/data/processed/Shared_Features_Study_5_FINAL.sav", to.data.frame = TRUE)

input_data_exp_6 <- 
  read.spss("../experiment 6/data/processed/Shared_Features_Study_6_FINAL.sav", to.data.frame = TRUE)

input_data_exp_7 <- 
  read.spss("../experiment 7/data/processed/Shared_Features_Study_7_FINAL.sav", to.data.frame = TRUE)

input_data_exp_8 <- 
  read.spss("../experiment 8/data/processed/Shared_Features_Study_8_FINAL.sav", to.data.frame = TRUE)

input_data_exp_9 <- 
  read.spss("../experiment 9/data/processed/Shared_Features_Study_9_FINAL.sav", to.data.frame = TRUE)


write_csv(input_data_exp_1, "../experiment 1/data/processed/data_spss_converted_to_csv.csv")
write_csv(input_data_exp_2, "../experiment 2/data/processed/data_spss_converted_to_csv.csv")
write_csv(input_data_exp_3, "../experiment 3/data/processed/data_spss_converted_to_csv.csv")
write_csv(input_data_exp_4, "../experiment 4/data/processed/data_spss_converted_to_csv.csv")
write_csv(input_data_exp_5, "../experiment 5/data/processed/data_spss_converted_to_csv.csv")
write_csv(input_data_exp_6, "../experiment 6/data/processed/data_spss_converted_to_csv.csv")
write_csv(input_data_exp_7, "../experiment 7/data/processed/data_spss_converted_to_csv.csv")
write_csv(input_data_exp_8, "../experiment 8/data/processed/data_spss_converted_to_csv.csv")
write_csv(input_data_exp_9, "../experiment 9/data/processed/data_spss_converted_to_csv.csv")

# tidy data
data_exp_1 <- read.csv("../experiment 1/data/processed/data_spss_converted_to_csv.csv") %>%
  mutate(intention = str_remove_all(Intentions_response, " "),
         intention = str_remove_all(intention, "Iwouldtry"),
         intention = as.factor(intention),
         color_valence_contingency_memory = ifelse(Total_CS_Color_Contingency_Score == 2, TRUE, FALSE),
         US_contingency_memory = ifelse(Total_US_Contingency_Score == 2, TRUE, FALSE),
         hypothesis_awareness = ifelse(Hypothesis_Awareness_recoded == 1, TRUE, FALSE),
         influence_awareness = ifelse(Influence_Awareness_recoded == 1, TRUE, FALSE),
         reactance_IAT = ifelse(Reactance_IAT == 1, TRUE, FALSE), 
         reactance_self_reports = ifelse(Reactance_Self_Reports == 1, TRUE, FALSE),
         demand_IAT = ifelse(Demand_IAT == 1, TRUE, FALSE), 
         demand_self_reports = ifelse(Demand_Self_Reports == 1, TRUE, FALSE)) %>%
  mutate(source_valence_condition = as.factor(str_replace_all(as.character(Color_Matching), " ", ""))) %>%
  select(Participant, 
         Age, 
         Gender,
         source_valence_condition,
         IAT_Score,
         EC_Effect_CS1_CS2_Difference_Score,
         intention,
         color_valence_contingency_memory,
         US_contingency_memory,
         hypothesis_awareness,
         influence_awareness,
         reactance_IAT,
         reactance_self_reports,
         demand_IAT,
         demand_self_reports) %>%
  # exclude participants with partial data
  na.omit()

data_exp_2 <- read.csv("../experiment 2/data/processed/data_spss_converted_to_csv.csv") %>%
  mutate(intention = str_remove_all(Intentions_response, " "),
         intention = str_remove_all(intention, "Iwouldtry"),
         intention = as.factor(intention),
         color_valence_contingency_memory = ifelse(Total_CS_Color_Contingency_Score == 2, TRUE, FALSE),
         US_contingency_memory = ifelse(Total_US_Contingency_Score == 2, TRUE, FALSE),
         hypothesis_awareness = ifelse(Hypothesis_Awareness_recoded == 1, TRUE, FALSE),
         influence_awareness = ifelse(Influence_Awareness_recoded == 1, TRUE, FALSE),
         reactance_IAT = ifelse(Reactance_IAT == 1, TRUE, FALSE), 
         reactance_self_reports = ifelse(Reactance_Self_Reports == 1, TRUE, FALSE),
         demand_IAT = ifelse(Demand_IAT == 1, TRUE, FALSE), 
         demand_self_reports = ifelse(Demand_Self_Reports == 1, TRUE, FALSE)) %>%
  mutate(source_valence_condition = as.factor(str_replace_all(as.character(Color_Matching), " ", ""))) %>%
  select(Participant,
         Age, 
         Gender,
         source_valence_condition,
         IAT_Score,
         EC_Effect_CS1_CS2_Difference_Score,
         intention,
         color_valence_contingency_memory,
         US_contingency_memory,
         hypothesis_awareness,
         influence_awareness,
         reactance_IAT,
         reactance_self_reports,
         demand_IAT,
         demand_self_reports) %>%
  # exclude participants with partial data
  na.omit()

data_exp_3 <- read.csv("../experiment 3/data/processed/data_spss_converted_to_csv.csv") %>%
  mutate(intention = str_remove_all(Intentions_response, " "),
         intention = str_remove_all(intention, "Iwouldtry"),
         intention = as.factor(intention),
         color_valence_contingency_memory = ifelse(Total_CS_Color_Contingency_Score == 2, TRUE, FALSE),
         US_contingency_memory = ifelse(Total_US_Contingency_Score == 2, TRUE, FALSE),
         hypothesis_awareness = ifelse(Hypothesis_Awareness_recoded == 1, TRUE, FALSE),
         influence_awareness = ifelse(Influence_Awareness_recoded == 1, TRUE, FALSE),
         reactance_IAT = ifelse(Reactance_IAT == 1, TRUE, FALSE), 
         reactance_self_reports = ifelse(Reactance_Self_Reports == 1, TRUE, FALSE),
         demand_IAT = ifelse(Demand_IAT == 1, TRUE, FALSE), 
         demand_self_reports = ifelse(Demand_Self_Reports == 1, TRUE, FALSE)) %>%
  mutate(source_valence_condition = as.factor(str_replace_all(as.character(Color_Matching), " ", ""))) %>%
  select(Participant, 
         Age, 
         Gender,
         source_valence_condition,
         IAT_Score,
         EC_Effect_CS1_CS2_Difference_Score,
         intention,
         color_valence_contingency_memory,
         US_contingency_memory,
         hypothesis_awareness,
         influence_awareness,
         reactance_IAT,
         reactance_self_reports,
         demand_IAT,
         demand_self_reports) %>%
  # exclude participants with partial data
  na.omit()

data_exp_4 <- read.csv("../experiment 4/data/processed/data_spss_converted_to_csv.csv") %>%
  mutate(intention = str_remove_all(Intentions_response, " "),
         intention = str_remove_all(intention, "Iwouldtry"),
         intention = as.factor(intention),
         color_valence_contingency_memory = ifelse(Total_CS_Size_Contingency_Score == 2, TRUE, FALSE),
         US_contingency_memory = ifelse(Total_US_Contingency_Score == 2, TRUE, FALSE),
         hypothesis_awareness = ifelse(Hypothesis_Awareness_recoded == 1, TRUE, FALSE),
         influence_awareness = ifelse(Influence_Awareness_recoded == 1, TRUE, FALSE),
         reactance_IAT = ifelse(Reactance_IAT == 1, TRUE, FALSE), 
         reactance_self_reports = ifelse(Reactance_Self_Reports == 1, TRUE, FALSE),
         demand_IAT = ifelse(Demand_IAT == 1, TRUE, FALSE), 
         demand_self_reports = ifelse(Demand_Self_Reports == 1, TRUE, FALSE)) %>%
  mutate(source_valence_condition = as.factor(str_replace_all(as.character(Size_Matching), " ", ""))) %>%
  select(Participant, 
         Age, 
         Gender,
         source_valence_condition,
         IAT_Score,
         EC_Effect_CS1_CS2_Difference_Score,
         intention,
         color_valence_contingency_memory,
         US_contingency_memory,
         hypothesis_awareness,
         influence_awareness,
         reactance_IAT,
         reactance_self_reports,
         demand_IAT,
         demand_self_reports) %>%
  # exclude participants with partial data
  na.omit()

data_exp_5 <- read.csv("../experiment 5/data/processed/data_spss_converted_to_csv.csv") %>%
  mutate(intention = str_remove_all(Intentions_response, " "),
         intention = str_remove_all(intention, "Iwouldtry"),
         intention = as.factor(intention),
         color_valence_contingency_memory = ifelse(Total_CS_Color_Contingency_Score == 4, TRUE, FALSE),
         US_contingency_memory = ifelse(Total_US_Contingency_Score == 2, TRUE, FALSE),
         hypothesis_awareness = ifelse(Hypothesis_Awareness_recoded == 1, TRUE, FALSE),
         influence_awareness = ifelse(Influence_Awareness_recoded == 1, TRUE, FALSE),
         color_training = ifelse(Total_Color_Training_Score == 4, TRUE, FALSE), 
         reactance_IAT = ifelse(Reactance_IAT == 1, TRUE, FALSE), 
         reactance_self_reports = ifelse(Reactance_Self_Reports == 1, TRUE, FALSE),
         demand_IAT = ifelse(Demand_IAT == 1, TRUE, FALSE), 
         demand_self_reports = ifelse(Demand_Self_Reports == 1, TRUE, FALSE)) %>%
  mutate(source_valence_condition = as.factor(str_replace_all(as.character(Color_Matching), " ", ""))) %>%
  select(Participant, 
         Age, 
         Gender,
         source_valence_condition,
         IAT_Score,
         EC_Effect_CS1_CS2_Difference_Score,
         intention,
         color_valence_contingency_memory,
         US_contingency_memory,
         hypothesis_awareness,
         influence_awareness,
         color_training,
         reactance_IAT,
         reactance_self_reports,
         demand_IAT,
         demand_self_reports) %>%
  # exclude participants with partial data
  na.omit()

data_exp_6 <- read.csv("../experiment 6/data/processed/data_spss_converted_to_csv.csv") %>%
  mutate(intention = str_remove_all(Intentions_response, " "),
         intention = str_remove_all(intention, "Iwouldtry"),
         intention = as.factor(intention),
         us_valence_contingency_memory = ifelse(Total_US_Valence_Contingency_Score == 2, TRUE, FALSE),
         CS_contingency_memory = ifelse(Total_CS_US_Contingency_Score == 2, TRUE, FALSE),
         hypothesis_awareness = ifelse(Hypothesis_Awareness_recoded == 1, TRUE, FALSE),
         influence_awareness = ifelse(Influence_Awareness_recoded == 1, TRUE, FALSE),
         reactance_IAT = ifelse(Reactance_IAT == 1, TRUE, FALSE), 
         reactance_self_reports = ifelse(Reactance_Self_Reports == 1, TRUE, FALSE),
         demand_IAT = ifelse(Demand_IAT_recoded == 1, TRUE, FALSE), 
         demand_self_reports = ifelse(Demand_Self_Reports_recoded == 1, TRUE, FALSE)) %>%
  mutate(source_valence_condition = as.factor(str_replace_all(as.character(Color_Matching), " ", ""))) %>%
  select(Participant, 
         Age, 
         Gender,
         source_valence_condition,
         IAT_Score,
         EC_Effect_CS1_CS2_Difference_Score,
         intention,
         us_valence_contingency_memory,
         CS_contingency_memory,
         hypothesis_awareness,
         influence_awareness,
         reactance_IAT,
         reactance_self_reports,
         demand_IAT,
         demand_self_reports) %>%
  # exclude participants with partial data
  na.omit()

data_exp_7 <- read.csv("../experiment 7/data/processed/data_spss_converted_to_csv.csv") %>%
  # remove the variables associated by the evaluative priming task which were calculated by hand in the SPSS file. 
  select(-EP_Morag_Score, -EP_Struan_Score, -EP_Score, -Reversed_EP_Score) %>%
  mutate(intention = str_remove_all(Intentions_response, " "),
         intention = str_remove_all(intention, "Iwouldtry"),
         intention = as.factor(intention),
         color_valence_contingency_memory = ifelse(Total_CS_Size_Contingency_Score == 2, TRUE, FALSE),
         US_contingency_memory = ifelse(Total_US_Contingency_Score == 2, TRUE, FALSE),
         hypothesis_awareness = ifelse(Hypothesis_Awareness_recoded == 1, TRUE, FALSE),
         influence_awareness = ifelse(Influence_Awareness_recoded == 1, TRUE, FALSE),
         reactance_IAT = ifelse(Reactance_IAT == 1, TRUE, FALSE), 
         reactance_self_reports = ifelse(Reactance_Self_Reports == 1, TRUE, FALSE),
         demand_IAT = ifelse(Demand_IAT == 1, TRUE, FALSE), 
         demand_self_reports = ifelse(Demand_Self_Reports == 1, TRUE, FALSE)) %>%
  mutate(source_valence_condition = as.factor(str_replace_all(as.character(Size_Matching), " ", ""))) %>%
  select(Participant, 
         Age, 
         Gender,
         source_valence_condition,
         EC_Effect_CS1_CS2_Difference_Score,
         intention,
         color_valence_contingency_memory,
         US_contingency_memory,
         hypothesis_awareness,
         influence_awareness,
         reactance_IAT,
         reactance_self_reports,
         demand_IAT,
         demand_self_reports) %>%
  # exclude participants with partial data
  na.omit() %>%
  # replace the EP variables with the EP scores calculated via the R script, which is more reproducible
  full_join(read.csv("../experiment 7/data/processed/processed_ep_data.csv"), by = c("Participant" = "subject"))

data_exp_8 <- read.csv("../experiment 8/data/processed/data_spss_converted_to_csv.csv") %>%
  mutate(US_contingency_memory = ifelse(US_Contingency_Awareness_recoded == 1, TRUE, FALSE),
         hypothesis_awareness = ifelse(Hypothesis_Awareness_recoded == 1, TRUE, FALSE),
         influence_awareness = ifelse(Influence_Awareness_recoded == 1, TRUE, FALSE),
         reactance_IAT = ifelse(Reactance_IAT == 1, TRUE, FALSE), 
         reactance_self_reports = ifelse(Reactance_Self_Reports == 1, TRUE, FALSE),
         demand_IAT = ifelse(Demand_IAT == 1, TRUE, FALSE), 
         demand_self_reports = ifelse(Demand_Self_Reports == 1, TRUE, FALSE),
         source_valence_condition = ifelse(str_detect(as.character(Stimulus_Identity), "Chris_Good_James_Bad"), "CS2_Positive_CS1_Negative",
                                           ifelse(str_detect(as.character(Stimulus_Identity), "Chris_Bad_James_Good"), "CS1_Positive_CS2_Negative", as.character(Stimulus_Identity)))) %>%
  mutate(Bag_Matching = as.factor(str_replace_all(as.character(Bag_Matching), " ", ""))) %>%
  select(Participant, 
         Age, 
         Gender,
         source_valence_condition,
         Bag_Matching,
         IAT_Score,
         EC_Effect_CS1_CS2_Difference_Score,
         US_contingency_memory,
         hypothesis_awareness,
         influence_awareness,
         reactance_IAT,
         reactance_self_reports,
         demand_IAT,
         demand_self_reports) %>%
  # exclude participants with partial data
  drop_na(-influence_awareness)

data_exp_9 <- read.csv("../experiment 9/data/processed/data_spss_converted_to_csv.csv") %>%
  mutate(US_contingency_memory = ifelse(US_Contingency_Awareness_recoded == 1, TRUE, FALSE),
         influence_awareness = ifelse(Influence_Awareness_recoded == 1, TRUE, FALSE),
         reactance_IAT = ifelse(Reactance_IAT == 1, TRUE, FALSE), 
         reactance_self_reports = ifelse(Reactance_Self_Reports == 1, TRUE, FALSE),
         demand_IAT = ifelse(Demand_IAT == 1, TRUE, FALSE), 
         demand_self_reports = ifelse(Demand_Self_Reports == 1, TRUE, FALSE),
         source_valence_condition = Stimulus_Identity) %>%
  mutate(Bag_Matching = as.factor(str_replace_all(as.character(Bag_Matching), " ", ""))) %>%
  select(Participant, 
         Age, 
         Gender,
         source_valence_condition,
         Bag_Matching,
         IAT_Score,
         EC_Effect_CS1_CS2_Difference_Score,
         US_contingency_memory,
         influence_awareness,
         reactance_IAT,
         reactance_self_reports,
         demand_IAT,
         demand_self_reports) %>%
  # exclude participants with partial data
  drop_na(-influence_awareness)

# write to disk
write_csv(data_exp_1, "../experiment 1/data/processed/data_for_analysis.csv")
write_csv(data_exp_2, "../experiment 2/data/processed/data_for_analysis.csv")
write_csv(data_exp_3, "../experiment 3/data/processed/data_for_analysis.csv")
write_csv(data_exp_4, "../experiment 4/data/processed/data_for_analysis.csv")
write_csv(data_exp_5, "../experiment 5/data/processed/data_for_analysis.csv")
write_csv(data_exp_6, "../experiment 6/data/processed/data_for_analysis.csv")
write_csv(data_exp_7, "../experiment 7/data/processed/data_for_analysis.csv")
write_csv(data_exp_8, "../experiment 8/data/processed/data_for_analysis.csv")
write_csv(data_exp_9, "../experiment 9/data/processed/data_for_analysis.csv")

```

